\chapter{Background and Related Work}
\label{ch:background}

This chapter reviews the technical background and related research that motivate
multimodal sensing-assisted user association and tracking in vehicular networks.
The discussion begins with beam management in high-frequency V2I links, then
surveys sensing-aided beam prediction and integrated
sensing and communication (ISAC) predictive beamforming. It further reviews
bird's-eye-view (BEV) multimodal fusion, cooperative perception, and the
identity-management problem that arises when sensing targets must be matched to
communication users. The chapter concludes by identifying the research gap
addressed by this thesis: a closed-loop framework that combines distributed
multimodal BEV perception, initial target-user association, temporal tracking,
and system-level communication evaluation.

The review is grounded in recent work on vision-, radar-, LiDAR-, and
multimodal sensing-aided beam prediction \cite{alrabeiah2019millimeterwavebasestations,xu2022computervisionaidedmmwave,charan2021visionpositionmultimodalbeamprediction,demirhan2021radaraided6gbeam,jiang2022lidaraidedfuturebeam}, ISAC predictive beamforming \cite{liu2020radarassistedpredictivebeamformingvehicular,yuan2020bayesianpredictivebeamformingvehicular,liu2022learningbasedpredictivebeamformingintegrated}, BEV fusion and cooperative perception \cite{zhou2019objectspoints,philion2020liftsplatshootencoding,liu2024bevfusionmultitaskmultisensorfusion,xu2022v2xvitvehicletoeverythingcooperativeperception}, and point-based tracking \cite{zhou2020trackingobjectspoints}.

\section{Vehicular Networks and Beam Management}
\label{sec:background-beam-management}

Vehicular networks support communication among vehicles, roadside
infrastructure, and network control entities in highly dynamic road
environments. In vehicle-to-infrastructure (V2I) communication, roadside base
stations (BSs) or road-side units provide wireless access to vehicles that may
move at high speed, change lanes, become temporarily blocked by other objects,
and enter or leave the coverage region within a short time. These mobility
patterns make link maintenance more difficult than in static or pedestrian
wireless scenarios. The wireless channel can vary rapidly not only because of
small-scale fading, but also because the relative geometry among the BS, the
vehicle, blockers, reflectors, and surrounding road structures changes over
time.

High-frequency systems, including millimeter-wave and future sub-terahertz
links, are especially sensitive to this geometry. Their large bandwidths and
large antenna arrays are attractive for vehicular applications, but the
available array gain is typically obtained through directional beams. A vehicle
must therefore be served by a suitable transmit or receive beam, and the chosen
beam must be updated as the vehicle moves. Beam misalignment can reduce the
effective link gain, while overly frequent beam training consumes time-frequency
resources that could otherwise be used for payload data. Beam management is thus
not only a physical-layer alignment problem; it directly affects spectral
efficiency, control overhead, and throughput.

Representative studies of V2I beam alignment and mobility-aware beam prediction
show that high-frequency vehicular links can benefit from visual, geometric, or
radar-like side information when beam measurements are costly or rapidly
outdated \cite{xu2022computervisionaidedmmwave,jiang2022lidaraidedfuturebeam,liu2020radarassistedpredictivebeamformingvehicular}.

\subsection{Beam Codebooks and Beam Training}
\label{subsec:background-codebooks-training}

Practical directional communication systems commonly restrict beam selection to
a finite codebook. Each beam in the codebook corresponds to a predefined spatial
direction or array weight vector. For a given vehicle user, the BS can evaluate
candidate beams through training or reference signals and select the beam that
provides a strong received power or effective channel gain. In a simplified
beam-management abstraction, the result of this process can be represented as a
per-beam power spectrum or beam quality vector, from which the best beam or a
small set of Top-K candidate beams can be selected.

In 5G-style systems, synchronization and reference signals such as
synchronization signal blocks (SSBs) and channel-state information reference
signals (CSI-RS) provide mechanisms for initial access, beam sweeping, channel
state acquisition, and later beam refinement. A full beam sweep is useful when
the system has little prior information, because it can scan the codebook and
observe the response of many beams. However, in a fast vehicular setting, a full
sweep can be expensive. It may occupy multiple time-frequency resources, and
the measured beam quality can become stale when the vehicle position or
blockage state changes before the next data transmission interval.

The overhead of beam training has two implications for this thesis. First, it
creates an incentive to use side information, such as sensing observations, to
narrow the beam search space. If sensing can reliably identify a small set of
candidate beams, communication measurements can be concentrated on that set
instead of the complete codebook. Second, the cost of beam training must be
reflected in communication evaluation. A method that improves raw beam
prediction accuracy may not improve overhead-adjusted throughput if it requires
frequent calibration signals, full sweeps, or recovery procedures. Conversely,
a slightly less accurate predictor may still be useful if it greatly reduces
measurement overhead while maintaining acceptable link quality.

Existing sensing-aided beam prediction studies commonly report Top-\(K\)
candidate accuracy and beam-searching overhead to quantify the benefit of
restricting the beam search space \cite{charan2021visionpositionmultimodalbeamprediction,alkhateeb2023deepsense6glargescalerealworld,charan2022multimodalbeampredictionchallenge,charan2023camerabasedmmwavebeam}.

\subsection{Mobility, Blockage, and Multi-User Operation}
\label{subsec:background-mobility-blockage}

Vehicular beam management is complicated by mobility, blockage, and multi-user
operation. Mobility changes the angle of departure, angle of arrival, path
length, Doppler shift, and relative visibility of propagation paths. Blockage
can suddenly make a previously strong beam unreliable, especially when trucks,
buses, buildings, or roadside objects obstruct a line-of-sight path. Multi-user
operation introduces an additional layer of ambiguity: several vehicles may be
visible in the same sensing field of view, and several users may have similar
beam power profiles when they occupy nearby angular sectors.

These factors affect both beam selection and user association. A BS may know
that a communication user is active through its access procedure, but a sensing
system may only observe a set of physical targets in the environment. The
mapping between a detected vehicle and a communication user is therefore not
automatic. A complete sensing-assisted beam-management system must decide not
only which beam appears suitable for a target, but also which target corresponds
to which communication user and how this relationship should be maintained over
time.

Prior work has also considered blockage-aware vision-aided prediction,
multi-candidate real-world beam prediction, and sequential beam tracking, which
motivate treating beam management as a temporally evolving multi-target problem
\cite{alrabeiah2019millimeterwavebasestations,charan2023camerabasedmmwavebeam,ma2026knowledgedistillationlightweightmultimodal,zeng2026bevfusionbasedframeworksequential}.

\section{Sensing-Aided Beam Prediction}
\label{sec:background-sensing-aided-beam-prediction}

Sensing-aided beam prediction uses information outside conventional channel
measurements to infer the likely communication beam for a user. The central
idea is that the wireless channel in a vehicular environment is strongly
coupled with physical geometry. If the system can observe the position, shape,
motion, or surrounding context of a vehicle, it may predict a small set of
promising beams before performing communication measurements. This reduces the
need for exhaustive beam sweeping and can support faster beam alignment in
dynamic road scenes.

Existing approaches can be organized by the sensing modality used. Position- or
GPS-aided methods use coarse user coordinates to estimate the angular relation
between the user and the BS. Camera-based methods use visual observations to
detect vehicles, infer scene context, or predict beam indices directly from
images. Radar-aided and LiDAR-aided methods exploit range, angle, Doppler, or
point-cloud geometry to capture the spatial relation between vehicles and
infrastructure. Multimodal methods combine several such sources, for example
camera images, position information, radar data, LiDAR point clouds, and
historical beam measurements.

The literature includes position-and-vision multimodal prediction,
camera-assisted prediction, radar-assisted prediction, LiDAR-aided future beam
prediction, and broader multimodal transformer formulations
\cite{charan2021visionpositionmultimodalbeamprediction,alrabeiah2019millimeterwavebasestations,demirhan2021radaraided6gbeam,jiang2022lidaraidedfuturebeam,tian2023multimodaltransformerswirelesscommunications}.

\subsection{Prediction Targets and Metrics}
\label{subsec:background-prediction-targets}

Most sensing-aided beam prediction studies formulate the task as a supervised
learning problem. The input is a sensing observation or a sequence of
observations, and the output is either a beam index, a ranked beam list, or a
beam power distribution over a codebook. A hard beam-index classifier is simple
to train and evaluate, but it does not describe how close the second or third
candidate beam is to the best beam. A ranked Top-K output is more flexible
because a communication system can test a small candidate set rather than rely
on a single predicted beam. A per-beam power distribution is richer still: it
can support Top-K selection, beam power loss analysis, and later modeling of
beam mismatch effects.

Common evaluation metrics include Top-1 accuracy, Top-K accuracy, beam power
loss, normalized received power, beam searching overhead, and sometimes
spectral efficiency or latency. These metrics are useful for evaluating whether
sensing can narrow the beam search. However, they do not always capture the
complete system impact. In particular, a Top-K accuracy value does not indicate
whether the selected target is the correct communication user, whether the user
identity remains stable across frames, or how a beam prediction error affects
multi-user precoding and throughput after accounting for training overhead.

The DeepSense 6G dataset and associated beam-prediction challenge established
real-world multimodal sensing and communication benchmarks in which Top-\(K\)
beam accuracy, beam power loss, and generalization are central evaluation
concerns \cite{alkhateeb2023deepsense6glargescalerealworld,charan2022multimodalbeampredictionchallenge}.

\subsection{From Single-Modal to Multimodal Prediction}
\label{subsec:background-multimodal-beam-prediction}

Single-modal sensing is attractive because it has a clear interface and a lower
implementation burden. For example, a camera can provide semantic information
about vehicles and lanes, while radar or point-cloud sensing can provide more
direct geometric measurements. Yet each modality has limitations. Cameras are
sensitive to lighting, weather, occlusion, calibration error, and field-of-view
coverage. Radar and ISAC-like point clouds can offer geometric cues but may be
sparse or noisy. Position information is easy to use when available, but it may
be inaccurate or delayed and may not describe blockers or local propagation
context.

Multimodal beam prediction attempts to compensate for these limitations by
combining complementary observations. Camera features can provide semantic and
appearance cues, point-cloud features can provide geometric structure, and
communication measurements can anchor the prediction to the actual beam
response. Transformer-based and other feature-fusion architectures have been
studied for this purpose, and recent work has also considered missing-modality
robustness, temporal modeling, and knowledge distillation. These directions
indicate that sensing-aided beam management is moving beyond simple beam-index
classification toward richer multimodal and temporal inference.

For the thesis problem, the key limitation of much of this literature is not
the lack of beam prediction itself, but the limited treatment of the full
closed-loop problem. Many studies assume that the sensing input already
corresponds to the communication user, or that a user position label is
available. In dense vehicular scenes, however, the sensing system may detect
multiple targets, only some of which are active communication users. This
requires target-user association and temporal tracking in addition to beam
prediction.

Recent studies have extended sensing-aided beam prediction toward multimodal
transformers, reinforcement learning, contextual bandits, missing-modality
robustness, knowledge distillation, and multi-candidate camera-based settings
\cite{tian2023multimodaltransformerswirelesscommunications,ghassemi2024multimodaltransformerreinforcementlearningbased,farzanullah2025beamselectionisacusing,wen2026amberadaptivemultimodalmask,ma2026knowledgedistillationlightweightmultimodal,charan2023camerabasedmmwavebeam}.

\section{ISAC Predictive Beamforming and Tracking}
\label{sec:background-isac-predictive-beamforming}

Integrated sensing and communication provides another route to mobility-aware
beam management. In ISAC systems, communication infrastructure is designed to
support both data transmission and environmental sensing. A BS may obtain
radar-like echoes, reflected signal samples, range-angle estimates, Doppler
information, or point-cloud-like observations from dual-function waveforms.
These sensing outputs can be used to estimate vehicle states and predict future
communication beams or beamforming vectors.

ISAC predictive beamforming is closely related to the problem studied in this
thesis because it explicitly connects sensing, tracking, and communication
performance. Classical state-estimation approaches use vehicle motion models
and filtering methods such as Kalman filtering, extended Kalman filtering, or
Bayesian message passing to predict angles, ranges, velocities, and future
beamforming directions. Learning-based approaches use historical channels,
sensing samples, or compact state representations to learn temporal dynamics
with recurrent neural networks, convolutional LSTMs, transformers, or
end-to-end neural beamformers. Some formulations optimize communication rate
under sensing constraints, while others use sensing to reduce beam alignment
overhead.

Representative ISAC studies include radar-assisted predictive beamforming,
Bayesian joint radar-communication beamforming, dynamic predictive beamforming
for extended vehicle targets, learning-based predictive beamforming, CLSTM-based
prediction, and end-to-end ISAC-enabled beamforming
\cite{liu2020radarassistedpredictivebeamformingvehicular,yuan2020bayesianpredictivebeamformingvehicular,du2021integratedsensingcommunicationsv2i,liu2022learningbasedpredictivebeamformingintegrated,liu2022deepclstmpredictivebeamforming,Wang_2023}.

\subsection{State Prediction and Communication Objectives}
\label{subsec:background-isac-state-objectives}

The value of ISAC sensing lies in its ability to provide state information that
is directly relevant to communication. Range, velocity, angle, and motion
pattern estimates can indicate how a beam should change over time. For
vehicular users, state prediction is particularly useful because future beam
quality may be more important than the beam measured in the current instant.
If the vehicle moves before the next data transmission, a purely reactive beam
selection can become outdated. Predictive beamforming attempts to anticipate
this evolution.

The communication objective in ISAC work is often expressed through received
power, achievable rate, sum rate, or beamforming gain. Some studies also
consider sensing performance, for example through estimation accuracy or
sensing constraints. These formulations are valuable for understanding the
communication-sensing tradeoff, but they usually begin from a communication or
radar-centric observation model. By contrast, this thesis uses an
overhead-adjusted ZF-based evaluation to expose how multimodal perception,
target-user association, and tracking errors affect a downstream multi-user
communication abstraction.

\subsection{Relation to This Thesis}
\label{subsec:background-isac-relation}

The ISAC literature provides important support for the premise that sensing can
serve communication in vehicular networks. It also motivates the use of
tracking, because beamforming decisions should reflect the temporal evolution
of vehicle states. However, this thesis considers a broader multimodal
observation setting. The BS may have an ISAC point cloud, but it may also have
multiview cameras, and surrounding sensing nodes may provide additional
camera observations. The resulting problem is not only to predict a future
beamforming vector from an ISAC echo, but also to detect vehicles in a shared
spatial representation, associate detections with communication users, and
maintain those identities over multiple frames.

This distinction shapes the role of ISAC in the thesis. ISAC sensing is treated
as one modality in a multimodal perception system rather than as the only
source of state information. Its geometric information complements
camera-derived scene features in the BEV representation. The
communication evaluation then asks how the resulting Top-K beam prediction,
association, and tracking decisions influence beam training overhead, beam
mismatch, zero-forcing (ZF) precoding, spectral efficiency, and
overhead-adjusted throughput.

\section{BEV Multimodal Fusion and Cooperative Perception}
\label{sec:background-bev-cooperative-perception}

Autonomous-driving perception has developed a rich set of tools for fusing
multiview images, point clouds, and multi-agent observations. These tools are
relevant to sensing-assisted communication because the wireless channel in
vehicular networks is tied to the physical road scene. A perception system that
can accurately represent vehicle positions, motion, and occlusion structure can
provide useful information for beam prediction and tracking.

BEV representation is especially suitable for roadside vehicular scenarios. In
a BEV coordinate frame, objects are represented in a ground-plane spatial grid
that is aligned with the road environment. Camera observations from different
viewpoints can be projected or lifted into this frame, and point-cloud
observations can be encoded in the same spatial coordinates. Once features are
placed in a common BEV space, detection, tracking, and beam prediction can be
implemented as spatial tasks over a shared feature map. This is attractive for
the thesis because beam quality is strongly related to the relative position
between the BS and the vehicle, while target-user association requires
consistent object locations across sensors and frames.

The BEV and cooperative-perception discussion builds on object-as-point
detection, tracking-as-points, camera-to-BEV lifting, unified BEV multisensor
fusion, V2X cooperative perception, and recent BEV-fusion-based sequential beam
prediction \cite{zhou2019objectspoints,zhou2020trackingobjectspoints,philion2020liftsplatshootencoding,liu2024bevfusionmultitaskmultisensorfusion,xu2022v2xvitvehicletoeverythingcooperativeperception,zeng2026bevfusionbasedframeworksequential}.

\subsection{BEV Fusion for Camera and Point-Cloud Observations}
\label{subsec:background-bev-fusion}

Camera-to-BEV methods use calibration and depth reasoning to transform image
features from perspective views into a top-down representation. Point-cloud
methods can encode geometric measurements directly in the same BEV grid. In
multimodal fusion, image features and point-cloud features are combined so that
semantic and geometric information can support the same downstream tasks. For
example, image features may help distinguish vehicle categories and visible
boundaries, while point-cloud features may provide depth and occupancy cues
that are more directly related to spatial localization.

This thesis adapts the BEV fusion idea to infrastructure-assisted wireless
communication. The camera modality consists of the multiview cameras mounted
on the serving BS and nearby sensing nodes (SNs). The ISAC modality consists of
the BS-side point cloud or point-cloud-like sensing output. A unified BEV
feature map provides a natural interface for two tasks that are often separated
in existing work: vehicle detection and per-target beam prediction. A
CenterNet-like detection head represents vehicles as points or centers in the
BEV grid, while a beam prediction head estimates a beam power distribution for
each detected target.

\subsection{Distributed and Cooperative Perception}
\label{subsec:background-cooperative-perception}

Cooperative perception extends single-agent perception by sharing observations
or intermediate features among multiple sensing agents. In road environments,
cooperation can improve coverage because different sensors observe the scene
from different viewpoints. It can also help with occlusion: a vehicle blocked
from one camera may remain visible from another sensor. V2X cooperative
perception research has studied feature fusion, pose errors, asynchronous
observations, heterogeneous sensors, and communication-efficient information
sharing among vehicles and infrastructure.

The BS-centric setting in this thesis has a related but communication-oriented
structure. For each serving BS, nearby SNs provide additional camera views.
Unlike communication users, these SNs are not necessarily serving data traffic;
their role is to enrich the environmental observation available to the BS. The
fusion problem therefore differs from standard autonomous-driving cooperative
perception. The final output is not only a set of detected vehicles, but also
beam-related information for the BS codebook and association information for
communication users. This motivates a BEV fusion framework whose downstream
objectives are communication-aware.

V2X cooperative perception and distributed sensing-aided networking provide
the conceptual basis for using observations from multiple infrastructure nodes
to enrich the BS-side representation \cite{xu2022v2xvitvehicletoeverythingcooperativeperception,imran2024environmentsemanticcommunicationenabling}.

\section{Target-User Association and Tracking in Sensing-Assisted Communication}
\label{sec:background-target-user-association-tracking}

Sensing-assisted beam prediction becomes substantially more difficult in
multi-vehicle scenes because sensing and communication systems use different
notions of identity. A sensing target is a physical object detected from
camera, ISAC, or fused BEV observations. A tracking identity is a temporal
hypothesis that links detections across frames. A communication user identity
is the identity used by the wireless system for access, scheduling, channel
measurement, and data transmission. These identities are related but not
identical. A vehicle may be detected by the sensing system without being an
active user, and an active communication user may be partially occluded or
temporarily missed by the sensing system.

This identity gap is often hidden in single-user or label-rich beam prediction
studies. If each sensing sample is already paired with the correct beam label,
the learning problem can be formulated as direct beam prediction. In a realistic
multi-user V2I scene, however, the BS may observe multiple vehicles and receive
beam measurements from multiple communication users. It must determine which
detected target corresponds to each user before a per-target beam prediction
can be used for communication decisions. This is the target-user association
problem.

Multi-candidate beam prediction and distributed sensing-aided networking
directly expose the ambiguity between multiple detected objects and the
communication entities that generate beam measurements
\cite{charan2023camerabasedmmwavebeam,imran2024environmentsemanticcommunicationenabling}.

\subsection{Initial Association from Beam Measurements}
\label{subsec:background-initial-association}

Initial access provides an opportunity to anchor sensing targets to
communication user identities. During an initial SSB beam sweep, the BS can
obtain a beam power spectrum for each communication user. At the same time, the
sensing network can detect vehicles and estimate a per-target beam distribution
from multimodal observations. If a detected target and a communication user
correspond to the same physical vehicle, their beam distributions should be
compatible under the BS codebook, subject to prediction error, sensing noise,
and channel variation. This suggests an association mechanism based on matching
communication beam measurements to predicted per-target beam distributions.

The association decision can also incorporate spatial priors, detection
confidence, temporal consistency, and constraints that prevent one target from
being assigned to multiple users. However, the matching process is inherently
uncertain. Nearby vehicles can have similar beam spectra, a blocked path can
alter the measured distribution, and sensing detections can be imperfect.
Therefore, target-user association is treated as a confidence-aware matching
component rather than a one-time deterministic label assignment. The association
cost combines beam-distribution similarity, BEV spatial consistency, and
detection confidence, and the resulting assignment is constrained to avoid
assigning one sensing target to multiple communication users.

\subsection{Tracking for Identity Maintenance and Beam Continuity}
\label{subsec:background-tracking-maintenance}

After initial association, the system must maintain the relationship between
the communication user and the sensing track. Repeating a full beam sweep in
every frame would reduce ambiguity but would also increase overhead. A more
efficient approach is to use tracking to propagate the user state over time and
to update it when new BEV detections are available. Tracking-by-detection
methods link detections across frames based on spatial proximity, motion
consistency, appearance, or learned displacement. Filtering methods maintain a
state estimate and predict the next state before measurement update.

For vehicular motion, an interacting multiple model (IMM) filter is a natural
candidate because vehicles can follow different motion modes, such as steady
motion, acceleration, braking, or turning. An IMM tracker maintains multiple
motion hypotheses and combines them according to their likelihoods. In the
thesis framework, the tracking state includes BEV position, velocity, and
motion-mode information. The predicted track can guide detection association and
beam selection in later frames. If tracking confidence degrades, the system can
trigger partial beam measurement or re-association rather than immediately
falling back to a full sweep.

The tracking component is inspired by point-based tracking in computer vision
and by predictive beamforming studies that use temporal vehicle-state evolution
to guide communication decisions \cite{zhou2020trackingobjectspoints,liu2020radarassistedpredictivebeamformingvehicular,yuan2020bayesianpredictivebeamformingvehicular,liu2022deepclstmpredictivebeamforming,ma2026knowledgedistillationlightweightmultimodal}. In the thesis framework, the IMM tracker uses multiple vehicle-motion hypotheses to support position prediction, detection association, confidence-aware track maintenance, and measurement-efficient beam recovery.

\section{Summary of Research Gap}
\label{sec:background-gap}

The reviewed areas show that the components needed for sensing-assisted
vehicular beam management have developed along several related but only
partially connected lines. Vehicular beam-management research clarifies the
overhead and mobility challenges of directional communication. Sensing-aided
beam prediction shows that camera, position, radar, LiDAR, point-cloud, and
multimodal observations can help narrow the beam search. ISAC predictive
beamforming connects sensing, state prediction, and communication objectives.
BEV fusion and cooperative perception provide mature tools for multi-sensor
and multi-agent scene understanding. Target association and tracking methods
address identity maintenance in dynamic scenes.

However, the thesis problem remains insufficiently covered when these
directions are considered as a closed-loop system. The following gaps motivate
the work developed in later chapters.

\begin{enumerate}
    \item Existing sensing-aided beam prediction studies often focus on a
    single sensing site, a limited set of modalities, or an already identified
    communication user. They do not fully address a BS-centric setting in which
    the serving BS fuses its own multiview cameras, BS-side ISAC point cloud,
    and nearby SN camera views in a unified BEV representation for per-target
    beam prediction.

    \item Existing ISAC predictive beamforming studies demonstrate the value of
    sensing and tracking for vehicular links, but they are usually formulated
    around radar echoes, reflected signal samples, historical channels, or
    state estimates. They less often incorporate camera-based multi-object
    perception, distributed sensing nodes, and explicit target-user association
    in the same framework.

    \item Existing BEV and cooperative perception methods provide strong
    spatial fusion tools, but their primary objectives are typically detection,
    segmentation, forecasting, or autonomous-driving scene understanding. They
    do not directly model BS codebook beam distributions, SSB-based initial
    association, or the propagation of beam prediction errors to communication
    metrics.

    \item Existing multi-candidate beam prediction and transmitter
    identification work begins to address the ambiguity between visual objects
    and communication users, but long-term identity maintenance through
    tracking and measurement-efficient re-association remains underdeveloped
    for multimodal distributed sensing-assisted vehicular networks.

    \item Existing evaluations often report Top-K beam accuracy, beam power
    loss, or achievable rate in isolation. A system-level evaluation loop that
    jointly considers detection, target-user association, tracking error, beam
    training overhead, beam mismatch, ZF precoding, spectral efficiency, and
    overhead-adjusted throughput is still needed for the research objective of
    this thesis.
\end{enumerate}

Accordingly, this thesis is positioned around a BS-centric multimodal
distributed sensing-assisted beam-management framework. The proposed framework
uses BS and SN camera observations together with BS-side ISAC point clouds to
construct a BEV representation, predicts per-target beam power distributions
and Top-K candidate beams, establishes an initial mapping between sensing
targets and communication users from SSB beam measurements, and maintains this
mapping through tracking over subsequent frames. The communication evaluation
then examines how the sensing and tracking decisions influence beam training
overhead and ZF-based throughput.

The comparison above indicates that the proposed thesis scope is closest to the
intersection of multimodal beam prediction, ISAC predictive beamforming,
BEV-based cooperative perception, and tracking-assisted identity maintenance
\cite{zeng2026bevfusionbasedframeworksequential,farzanullah2025beamselectionisacusing,imran2024environmentsemanticcommunicationenabling,zhou2020trackingobjectspoints}.
