\chapter{Multimodal Simulation System and Experimental Evaluation}
\label{ch:experiments}

\section{Multimodal Simulation System}
\label{sec:experiments-simulation-system}

This chapter describes the simulation system and experimental methodology used
to evaluate the proposed multimodal sensing-assisted beam management framework.
The evaluation is designed to connect three levels of evidence: the quality of
vehicle perception in the bird's-eye-view (BEV) representation, the reliability
of target-user association and tracking, and the resulting communication
performance under a simplified beam management and zero-forcing (ZF) precoding
abstraction. Since the final experimental results are not yet available, the
result-oriented sections in this chapter are retained as structured
TODO[needs-evidence] placeholders rather than being written as conclusions.

\subsection{Simulation Pipeline Overview}
\label{subsec:experiments-pipeline-overview}

The simulation system is intended to generate synchronized multimodal sensing
observations and communication labels for a roadside vehicular network. The
pipeline follows the same high-level philosophy as multimodal wireless digital
twin workflows such as \texttt{Multi-modal-beam-twin} and
\texttt{Multimodal-Wireless}: a driving simulator is used to define traffic
motion and sensor observations, a graphics reconstruction stage prepares
geometry and material information, and a ray-tracing engine generates wireless
channels and beam-related labels.

In the planned implementation, CARLA provides the road layout, vehicle traffic,
camera sensors, and per-frame object states. The generated scene states are then
converted into a reconstruction format suitable for Blender and Mitsuba, where
the visual scene, object geometry, and material-related information can be
organized for rendering and ray-tracing preparation. Sionna RT is subsequently
used to compute multipath propagation, channel coefficients, path parameters,
and beam response labels for the service base station (BS) and vehicle users.
This pipeline is not intended to emulate the full 5G NR protocol stack. Instead,
it provides a controllable and reproducible environment for studying how
multimodal sensing affects beam prediction, target-user association, tracking,
and system-level communication metrics.

TODO[needs-evidence]: Confirm the exact simulator versions, adapted codebase,
scene conversion scripts, and file formats used in the final implementation.

\subsection{Road Traffic and Sensor Generation in CARLA}
\label{subsec:experiments-carla-generation}

CARLA is used to instantiate the road traffic scene and produce the time-indexed
states required by both the sensing and communication evaluations. Each frame
contains the poses of vehicles, the locations of roadside infrastructure, and
the outputs of multiple virtual sensors. The service BS is equipped with
multiple downward-looking camera views, and each cooperative sensing node (SN)
also provides multiple camera views over the road area. These camera streams
serve as the visual modality for BEV-based perception.

The BS-side ISAC modality is represented by an ISAC-like point cloud. In the
current research plan, this point cloud is treated as a geometric sensing
observation available at the BS and is used together with the camera modality in
the multimodal BEV fusion module. The exact procedure for generating this
ISAC-like point cloud remains implementation-dependent: it may be produced by a
simulated sensing process, an equivalent geometric point-cloud generator, or a
proxy derived from simulator state. This choice affects the realism of the
sensing modality and therefore must be documented explicitly before final
experiments are reported.

TODO[unstable-method]: Specify the final ISAC-like point-cloud generation
method, including its coordinate frame, sampling density, noise model, and
relationship to the BS-side sensing capability.

\subsection{Scene Reconstruction and Ray-Tracing Channel Generation}
\label{subsec:experiments-reconstruction-rt}

After CARLA generates the dynamic traffic state, the scene is reconstructed or
exported for Blender and Mitsuba so that the visual geometry and material
properties are available to the wireless ray-tracing stage. The reconstruction
stage links the simulated road layout, vehicle poses, static objects, and
infrastructure locations to a representation that can be consumed by Sionna RT.
This design allows the same traffic frame to support both multimodal perception
inputs and communication-channel labels.

Sionna RT is used to compute the propagation paths between the service BS and
vehicle users. For each user and frame, the channel generation stage is expected
to provide channel coefficients, path parameters, and a beam power distribution
over the BS beam codebook. The beam with the largest response can be used as the
best-beam label, while the full beam power distribution can supervise or
evaluate per-target beam prediction. These labels are also used by the
communication evaluation module to estimate the effect of correct or incorrect
Top-K beam selection.

TODO[needs-evidence]: Fix the ray-tracing frequency, antenna configuration,
beam codebook, material assumptions, path-depth setting, and channel storage
format before reporting quantitative results.

\subsection{Generated Data Products}
\label{subsec:experiments-data-products}

The output of the simulation pipeline is a multimodal sequence dataset. Each
sample is associated with a service BS, a time frame, a set of cooperative SNs,
and the vehicle users visible or relevant to the BS service region. The planned
data products include:

\begin{itemize}
    \item synchronized BS and SN camera images;
    \item BS-side ISAC-like point clouds;
    \item vehicle poses, velocities, trajectories, and object annotations;
    \item camera calibration and infrastructure pose metadata;
    \item reconstructed scene descriptions for rendering and ray tracing;
    \item channel coefficients and path parameters generated by Sionna RT;
    \item per-user beam power distributions and best-beam labels;
    \item communication-side beam measurements used for initial target-user
    association or later calibration.
\end{itemize}

These products support training and evaluation of the BEV detection module, the
per-target beam prediction head, the target-user association procedure, the IMM
tracking module, and the communication performance abstraction. The exact
dataset schema should remain traceable from raw simulation state to final model
inputs so that detection errors, beam-label errors, and communication-metric
errors can be analyzed separately.

\section{Scenario and Dataset Construction}
\label{sec:experiments-dataset-construction}

\subsection{Roadside Network Configuration}
\label{subsec:experiments-network-configuration}

The evaluation considers a roadside vehicular network with one or more BSs,
multiple cooperative SNs, and vehicle users moving through the road area. For
each service BS, a local cooperative sensing region is formed by selecting a set
of nearby SNs. The BS provides communication service and BS-side sensing, while
the SNs provide additional camera observations and do not directly serve users
in the communication model.

The final scenario configuration must specify the road topology, BS and SN
locations, sensor placements, camera orientations, field-of-view settings,
vehicle traffic patterns, and the temporal sampling rate. These values are not
yet fixed in the research brief and therefore should not be inferred in the
thesis text.

TODO[needs-evidence]: Add the final scenario table, including the number of
scenes, BSs, SNs, vehicles, frames, weather or illumination conditions, and
traffic-density settings.

\subsection{Multimodal Sample Construction}
\label{subsec:experiments-sample-construction}

For each frame, the camera and ISAC-like point-cloud observations are transformed
into coordinate systems compatible with BEV fusion. Camera metadata records the
intrinsic and extrinsic parameters of each BS and SN view, while point-cloud
metadata records the BS-centered sensing coordinate frame. Vehicle annotations
provide BEV locations and, where available, object extents and motion states.
These annotations enable the detection and tracking modules to be evaluated
independently from the communication labels.

Beam labels are generated from the ray-tracing output. For each vehicle user and
service BS, the per-beam response over the codebook defines the beam power
distribution. The Top-K candidate-beam set is obtained by ranking this
distribution. During initial access, a communication-side SSB beam sweep power
spectrum is assumed to be available for target-user association. During later
frames, the framework primarily uses sensing-assisted Top-K prediction and
tracking, with partial measurements reserved for calibration or recovery.

TODO[unstable-method]: Define the final synchronization tolerance, BEV grid
range, BEV resolution, beam-label normalization, and mapping between detected
targets and ray-traced vehicle identities.

\subsection{Training, Validation, and Test Splits}
\label{subsec:experiments-data-splits}

The dataset should be partitioned into training, validation, and test splits in
a way that separates model selection from final evaluation. The split design
should avoid leakage across temporally adjacent frames when evaluating tracking
and should, where possible, test generalization across traffic conditions,
vehicle densities, sensor visibility, or road layouts. If multiple scenarios
are generated, scenario-level splits should be considered in addition to
frame-level splits.

TODO[needs-evidence]: Specify the final split strategy, dataset sizes, sequence
lengths, and whether the test set contains unseen scenes, unseen traffic
patterns, or unseen sensor layouts.

\section{Baselines}
\label{sec:experiments-baselines}

The baselines are designed to isolate the effects of communication-only
measurement, visual sensing, ISAC-like sensing, distributed sensing, and
tracking. Each baseline should be evaluated using the same scenario splits,
beam codebook, channel labels, and communication metric definitions as the
proposed framework.

\subsection{Communication-Only Baselines}
\label{subsec:experiments-communication-baselines}

The communication-only full beam sweep baseline performs a complete beam sweep
at every decision epoch. It serves as a high-overhead reference for beam
selection because it does not rely on sensing prediction or tracking. The
communication-only partial sweep baseline measures only a subset of beams and
therefore represents a lower-overhead but potentially less reliable
communication-only alternative.

TODO[needs-evidence]: Define the exact full-sweep and partial-sweep protocols,
including the measured beam sets, measurement periodicity, and overhead
accounting.

\subsection{Sensing Modality Baselines}
\label{subsec:experiments-sensing-baselines}

The camera-only BEV beam prediction baseline uses BS and SN camera views but
does not use the BS-side ISAC-like point cloud. The ISAC-only baseline uses the
BS-side point cloud without camera observations. Comparing these baselines with
the proposed multimodal setting evaluates whether the two modalities provide
complementary information for detection, localization, and beam prediction.

The single-site sensing baseline uses only the service BS sensors and excludes
the cooperative SN camera views. This baseline tests the value of distributed
sensing, especially under occlusion or limited BS camera coverage.

TODO[needs-evidence]: Ensure that modality baselines use fair model capacity,
training data, and label definitions relative to the proposed multimodal model.

\subsection{Tracking and Association Baselines}
\label{subsec:experiments-tracking-baselines}

The no-tracking variant performs per-frame detection and beam prediction without
maintaining an IMM tracking state. It evaluates whether temporal prediction and
track-level identity maintenance improve target-user association and beam
selection continuity. Additional variants may remove communication-assisted
initial association or replace the proposed association cost with a simpler
matching rule once the final method is fixed.

TODO[unstable-method]: Define the final association variants after the matching
cost, IMM motion models, gating thresholds, and recovery rules are stabilized.

\subsection{Proposed Framework}
\label{subsec:experiments-proposed-framework}

The proposed framework uses the service BS camera views, cooperative SN camera
views, BS-side ISAC-like point clouds, SSB-based initial target-user
association, IMM tracking, and sensing-assisted Top-K beam prediction. It is
evaluated against the above baselines across perception, association, tracking,
beam management, and communication metrics.

\section{Evaluation Metrics}
\label{sec:experiments-metrics}

\subsection{Perception, Association, and Tracking Metrics}
\label{subsec:experiments-perception-metrics}

Vehicle perception is evaluated using detection accuracy or mean average
precision, together with BEV localization error. These metrics measure whether
the multimodal BEV representation can identify vehicles and localize them in the
roadside coordinate frame. When object extents are available, localization
metrics should be complemented by box-level detection measures.

Target-user association is evaluated by comparing the estimated mapping between
sensing targets and communication user identities against the simulation ground
truth. Tracking is evaluated using identity consistency and prediction error in
the BEV plane. These metrics are important because a correct beam prediction for
the wrong user can still degrade the communication evaluation.

TODO[needs-evidence]: Specify the exact detection, association, and tracking
metric formulas and any matching thresholds used in the evaluation scripts.

\subsection{Beam Management Metrics}
\label{subsec:experiments-beam-metrics}

Beam prediction is evaluated using Top-1 and Top-K beam accuracy, where a
prediction is correct if the ground-truth best beam or another defined valid
beam lies within the predicted candidate set. The evaluation also reports beam
power prediction error when the model outputs a full per-beam distribution. Beam
training overhead is measured by the amount of beam measurement required by each
scheme relative to its decision interval.

Because the proposed method uses sensing and tracking to reduce repeated full
beam sweeping, the beam management metrics should be interpreted jointly:
high Top-K accuracy is valuable only if it is achieved with lower measurement
overhead and without causing excessive reassociation or recovery events.

TODO[needs-evidence]: Define whether beam correctness is based only on the
single strongest beam or on a power-loss tolerance around the best beam.

\subsection{Communication Performance Metrics}
\label{subsec:experiments-communication-metrics}

Communication performance is evaluated using effective SINR under ZF precoding,
spectral efficiency, user throughput, system sum throughput, and
overhead-adjusted throughput. The communication model uses the ray-traced or
equivalent channel labels to estimate the effect of selected beams on the
multiuser effective channel. If the predicted Top-K set contains an acceptable
beam, the system can perform CSI acquisition or PMI selection within a smaller
candidate set. If the predicted set misses the effective beam, a beam mismatch
penalty is applied before computing the ZF-based SINR and throughput metrics.

The spectral efficiency for a user can be expressed generically as a function of
the effective SINR, for example through a Shannon-style mapping. The final
overhead-adjusted throughput should additionally subtract the time-frequency
resources consumed by beam training or calibration measurements. The exact
overhead model is not yet fixed and must be finalized before quantitative
claims are made.

TODO[unstable-method]: Fix the mathematical relationship between beam mismatch,
CSI/PMI degradation, ZF SINR, spectral efficiency, and overhead-adjusted
throughput.

\section{Main Results}
\label{sec:experiments-main-results}

\subsection{Detection and Beam Prediction Results}
\label{subsec:experiments-main-detection-beam}

TODO[needs-evidence]: Report detection accuracy, BEV localization error,
Top-1 beam accuracy, Top-K beam accuracy, and beam power prediction error for
the proposed framework and all relevant baselines. Include tables or figures
only after the results are recorded in \texttt{docs/work\_brief.md}.

\subsection{Association and Tracking Results}
\label{subsec:experiments-main-association-tracking}

TODO[needs-evidence]: Report target-user association accuracy, tracking identity
consistency, tracking prediction error, reassociation frequency, and failure
cases. The discussion should distinguish errors caused by missed detections,
ambiguous beam spectra, tracking drift, and communication-side measurement
noise.

\subsection{Communication-Level Results}
\label{subsec:experiments-main-communication}

TODO[needs-evidence]: Report effective SINR, spectral efficiency, user
throughput, system sum throughput, and overhead-adjusted throughput. Do not
state that the proposed method improves throughput until the full metric
definition, baselines, and numerical results are available.

\section{Ablation Studies}
\label{sec:experiments-ablation-studies}

The ablation studies are intended to identify which components of the proposed
framework contribute to the final system behavior. The planned ablations remove
or modify one component at a time while keeping the scenario, labels, codebook,
and communication evaluation fixed.

\subsection{Modality and Distributed-Sensing Ablations}
\label{subsec:experiments-ablation-modalities}

TODO[needs-evidence]: Compare the proposed multimodal model with camera-only,
ISAC-only, and single-site sensing variants. The analysis should report how
each modality affects vehicle detection, BEV localization, beam prediction, and
communication metrics under the same test split.

\subsection{Tracking and Association Ablations}
\label{subsec:experiments-ablation-tracking-association}

TODO[needs-evidence]: Compare the full framework with a no-tracking variant and
with alternative association rules once those rules are fixed. The analysis
should explain whether errors originate from the initial SSB-based association,
the tracking update, or the later beam maintenance step.

\subsection{Beam Measurement Ablations}
\label{subsec:experiments-ablation-measurement}

TODO[needs-evidence]: Compare full beam sweep, partial beam measurement, and
sensing-assisted Top-K beam selection under the same overhead accounting model.
The analysis should report both beam prediction accuracy and
overhead-adjusted communication performance.

\section{Sensitivity and Robustness Analysis}
\label{sec:experiments-sensitivity}

Sensitivity analysis evaluates whether the framework remains reliable when key
system assumptions vary. The planned factors include the number of candidate
beams in Top-K selection, the number and placement of cooperative SNs, vehicle
density, vehicle speed, occlusion level, camera calibration error,
synchronization error, point-cloud sparsity, point-cloud noise, beam codebook
size, and the strength of the beam mismatch penalty in the communication model.

TODO[needs-evidence]: Report sensitivity curves or tables for the above factors
after the final simulation configuration and evaluation scripts are available.

TODO[unstable-method]: Decide whether robustness tests use controlled synthetic
perturbations, naturally varied simulation scenarios, or both.

\section{Discussion and Limitations}
\label{sec:experiments-discussion}

The planned evaluation is designed to show how multimodal distributed sensing
can support beam management beyond isolated beam-index prediction. However, the
interpretation of the final results must remain tied to the assumptions of the
simulation system and the communication abstraction. First, the CARLA,
Blender/Mitsuba, and Sionna RT pipeline may not fully reproduce the statistics
of real roadside sensing and high-frequency propagation. Domain gaps may arise
from simplified vehicle materials, idealized sensor calibration, limited weather
or illumination diversity, and the absence of real hardware impairments.

Second, the BS-side ISAC-like point cloud is a simulation abstraction unless it
is generated by a validated ISAC sensing model. Its density, noise, angular
resolution, and occlusion behavior can strongly affect the apparent benefit of
the ISAC modality. Third, the communication evaluation uses a simplified beam
management and ZF precoding model rather than a full 5G NR protocol-level
simulation. Consequently, overhead-adjusted throughput should be interpreted as
a system-level abstraction for comparing beam management strategies, not as a
direct deployment throughput prediction.

Finally, target-user association and tracking errors can propagate into the
communication evaluation. A method may predict a plausible beam distribution for
a detected vehicle but still assign it to the wrong communication user. For this
reason, the final analysis should report perception, association, tracking, and
communication metrics together, rather than using throughput alone as the
primary evidence.

TODO[needs-evidence]: Extend this discussion with observed success cases,
failure cases, and limitations after the main, ablation, and sensitivity
experiments are completed.
