\chapter{Introduction}
\label{ch:introduction}

\section{Background}
\label{sec:introduction-background}

Vehicular networks are a key component of connected mobility and intelligent
transportation systems. Vehicle-to-infrastructure (V2I) links are expected to
support data-intensive and delay-sensitive services while vehicles move through
road environments whose geometry, visibility, and propagation conditions change
continuously. Millimetre-wave and other high-frequency bands provide the
bandwidth required by these services, but their array gain depends on narrow and
accurately aligned beams. A communication link must therefore be established and
maintained while the relative angle, range, blockage state, and dominant
propagation paths between a base station (BS) and a vehicle evolve rapidly
\cite{xu2022computervisionaidedmmwave,liu2020radarassistedpredictivebeamformingvehicular}.

Conventional beam management obtains communication evidence through
synchronization signal block (SSB) sweeps, channel-state-information
reference-signal (CSI-RS) measurements, and subsequent channel-state-information
acquisition and refinement. These procedures are indispensable at initial access
and whenever an existing link becomes uncertain. Their cost, however, grows with
the search space and with the frequency at which measurements must be repeated.
In a dynamic road scene, a beam measurement may become stale before it supports
the next data transmission. Repeated exhaustive scanning mitigates this
uncertainty, but consumes time--frequency resources that could otherwise carry
payload data. Consequently, vehicular beam alignment is not solely a problem of
identifying a favourable beam index; it is a communication decision that must
balance candidate-set quality, CSI aging, measurement overhead, and service
reliability \cite{charan2021visionpositionmultimodalbeamprediction,alkhateeb2023deepsense6glargescalerealworld,charan2023camerabasedmmwavebeam}.

Roadside infrastructure can observe the physical environment in which the
wireless link is formed. Cameras provide semantic and visibility cues, whereas
radar-, LiDAR-, and integrated sensing and communication (ISAC)-like
observations provide geometric information about vehicle position and motion.
Such information has been used to assist beam alignment, blockage prediction,
and future-beam prediction \cite{alrabeiah2019millimeterwavebasestations,demirhan2021radaraided6gbeam,jiang2022lidaraidedfuturebeam}. Multimodal learning and
predictive beamforming further indicate that environmental observations can
reduce the communication measurements needed to locate useful beams
\cite{tian2023multimodaltransformerswirelesscommunications,liu2022learningbasedpredictivebeamformingintegrated,farzanullah2025beamselectionisacusing}.

The value of sensing is particularly compelling in a road environment that
extends beyond the field of view of a single sensor. A serving BS can collect
multiview camera observations locally, neighbouring sensing nodes (SNs) can
offer complementary views of occluded or distant road segments, and a BS-local
ISAC point cloud can supply geometric cues unavailable from images alone. A
target-BS-centered bird's-eye-view (BEV) representation provides a common local
frame in which these heterogeneous observations can be aligned. BEV methods have
proved effective for camera--geometric fusion and cooperative perception
\cite{philion2020liftsplatshootencoding,liu2024bevfusionmultitaskmultisensorfusion,xu2022v2xvitvehicletoeverythingcooperativeperception}; their use in the present setting links
wide-area environment perception to the beam codebook of the serving BS.

Nevertheless, sensing information cannot be used as a direct substitute for
communication evidence. A sensing system observes physical vehicles in the road
scene, whereas the communication system operates on user equipment (UE)
identities. The difference is fundamental in a multi-vehicle setting: a model
may correctly detect several vehicles and predict a plausible beam-quality
distribution for each of them, yet none of these predictions is useful for
user-specific beam alignment until it is assigned to the correct UE. The central
question of this thesis is therefore how multimodal and cross-node sensing can
support beam alignment over a broad and changing road environment while ensuring
that a sensing-derived beam hint is associated with the communication user it is
intended to serve.

\section{Challenges}
\label{sec:introduction-challenges}

The first challenge is to exploit multimodal and cross-node sensing
complementarity under changing observation conditions. A single camera may be
limited by field of view, illumination, weather, or occlusion, while a point
cloud may be sparse, noisy, or geometrically incomplete. Similarly, the serving
BS may have limited visibility of road segments that are observable from a
neighbouring SN. Simply increasing the number of sensors does not by itself
produce a communication-relevant representation: the observations must be
spatially aligned, temporally coherent, and fused in a manner that retains both
semantic and geometric information. The resulting representation must support
vehicle detection and a conditional beam-quality ranking over the codebook in
the target BS's local service region. This requirement goes beyond single-modal
beam prediction because it asks whether complementary sensing can remain useful
across variations in coverage, visibility, blockage, and weather.

The second challenge is sensing target-to-user association. Beam prediction
studies commonly evaluate a sensing sample that is already paired with the
corresponding communication link. In operational V2I beam alignment, however,
the detector produces a set of physical sensing targets, whereas the BS receives
SSB and CSI-RS measurements indexed by communication UEs. The two sets need not
have the same cardinality: some observed vehicles may be inactive users, an
active UE may be temporarily unobserved, and nearby vehicles may have similar
beam signatures. A beam-quality distribution predicted for the correct physical
vehicle still leads to an incorrect beam-alignment action if it is assigned to a
different UE. Sensing target-to-user association is thus not a bookkeeping
operation after beam prediction; it is the mechanism that makes sensing-derived
beam information applicable to a particular communication link. This distinction
is especially important relative to beam-alignment formulations that assume UE
identity or link correspondence is available at the sensing input
\cite{charan2023camerabasedmmwavebeam,imran2024environmentsemanticcommunicationenabling}.

The third challenge is maintaining the target-to-user correspondence over time.
After an initial association, vehicle motion, short-term occlusion, missed
detections, and interactions among nearby targets can invalidate a correspondence
that was previously credible. The required mechanism is not visual recognition
of a UE identity. Rather, it is a multi-object state-estimation and data-
association process that preserves the temporal correspondence between an
unbound perception track and a communication UE, and that requests a new
communication measurement when the correspondence is no longer reliable.
Classical filtering and tracking approaches, together with predictive
beamforming research, motivate this temporal treatment of vehicle state
\cite{zhou2020trackingobjectspoints,yuan2020bayesianpredictivebeamformingvehicular,liu2022deepclstmpredictivebeamforming}. Within the present thesis, correspondence
maintenance is important because it determines whether a beam hint remains
assigned to the correct user across successive beam-alignment decisions.

The fourth challenge is to use sensing conservatively in the communication
decision. A candidate set may contain a useful beam but still be unsuitable when
the target-to-user association is ambiguous, the current observation is
unreliable, or the beam-quality distribution is diffuse. Conversely, a small
candidate set can reduce CSI-RS resources only if the retained beams preserve
sufficient link quality for the correct UE. A meaningful policy must therefore
assess the reliability of the association and the current sensing evidence,
apply sensing-derived candidates only when that evidence is credible, and retain
conventional refinement otherwise. Its evaluation must connect candidate recall
and CSI-RS overhead with effective rate, lower-tail user rate, and outage,
rather than inferring communication benefit from Top-\(K\) accuracy alone.

These challenges reveal two connected requirements for sensing-assisted
vehicular beam alignment: broad, condition-resilient environmental perception
through multimodal and cross-node observations, and identity-consistent use of
that perception through sensing target-to-user association and correspondence
maintenance. The framework developed in this thesis addresses both requirements
within a common measurement-aware communication procedure.

\section{Research Objective}
\label{sec:introduction-objective}

The objective of this thesis is to develop a BS-centric multimodal
sensing-assisted beam-alignment framework that uses complementary environmental
observations to reduce the CSI-RS measurement search space for the correct UE.
For every target BS, the framework fuses multiview camera observations at the
target BS and neighbouring SNs with a BS-local ISAC point cloud in a shared BEV
frame. A joint perception model detects vehicles and predicts a 192-way CSI
beam-quality distribution at each detected target. The distribution is intended
to rank beams as measurement candidates; it is not treated as a direct
replacement for the beam selected through communication measurement.

The second objective is to establish sensing target-to-user correspondence
without inserting a UE identifier or an oracle link coordinate into the
perception model. During initial access, after a serving-cell change, or when an
existing correspondence has lost credibility, conventional SSB and CSI-RS
measurements remain available. The measured beam evidence is associated with the
beam likelihood predicted for currently observed perception tracks. A one-to-one
association, constrained by the SSB-parent relation and its reliability, binds a
communication UE to an appropriate sensing track. Multi-object state estimation
then maintains the temporal correspondence between subsequent detections and the
bound UE. This construction makes the association between a physical sensing
target and a communication user an explicit and testable component of beam
alignment.

The third objective is to convert a reliable correspondence into a conservative
candidate-measurement decision. Only a currently observed target with a credible
target-to-user correspondence provides a fixed-size or adaptive set of CSI-RS
candidates. The UE selects a service beam from the candidates that are actually
measured. When the evidence is insufficient, the procedure falls back to
conventional refinement. The framework consequently separates three distinct
quantities: the beam-quality distribution exported by the perception model, the
distribution used for sensing target-to-user association, and the number of
beams measured by CSI-RS. This separation prevents a large model output from
being mistaken for a small pilot budget.

The study is scoped to a target-BS-centered local service region. A vehicle that
enters a new serving cell establishes a new local correspondence; the framework
does not assume a global multi-BS identity. Its system-level evaluation uses a
48-beam SSB codebook, a 192-beam CSI codebook, and common propagation, Doppler,
scheduling, power, regularized zero-forcing (RZF), and resource-accounting
assumptions across compared policies. The evaluation examines a chain of
evidence from multimodal perception and beam-quality ranking, through sensing
target-to-user association and correspondence maintenance, to candidate recall,
pilot overhead, effective rate, lower-tail rate, and outage. Ground-truth
identities and detections serve only diagnostic and upper-bound roles; the
formal decision path relies on sensing and communication measurements available
to the BS.

\section{Contributions}
\label{sec:introduction-contributions}

This thesis makes the following contributions.

\begin{enumerate}
    \item A target-BS-centered multimodal and cross-node learning formulation is
    developed for joint vehicle detection and 192-way CSI beam-quality
    prediction. By fusing camera observations from the target BS and neighbouring
    SNs with a BS-local ISAC point cloud in a common BEV grid, the formulation
    aligns object-level perception and link-level supervision and enables the
    complementarity of sensing modalities and viewpoints to be evaluated under
    varying observation conditions.

    \item A CSI power-distribution and ranking-based beam-supervision strategy
    is formulated in place of strongest-beam classification alone. The predicted
    distribution supports candidate ranking, confidence characterization, and
    beam-likelihood evaluation for sensing target-to-user association. Its value
    is assessed through controlled comparisons with strongest-beam and
    distribution-only supervision using beam-ranking and calibration measures.

    \item A sensing target-to-user association framework is introduced for
    identity-consistent beam alignment. The framework separates unbound
    perception outputs from communication UEs, maintains per-BS multi-object
    perception tracks, and uses conventional measurements for initial and
    recovery association. SSB-parent consistency, one-to-one assignment,
    reliability assessment, and conventional fallback ensure that a sensing-
    derived beam hint is used only when it has credible correspondence to the
    intended UE.

    \item A layered evaluation methodology is established to examine the system
    consequence of sensing-assisted beam alignment. The methodology jointly
    reports perception quality, beam-distribution quality, sensing target-to-user
    association, correspondence maintenance, candidate recall, CSI-RS overhead,
    RZF-based effective rate, lower-tail rate, and outage under a common resource
    model. It thereby distinguishes a useful beam ranking from a beam hint that
    is both correctly associated and beneficial to communication.
\end{enumerate}

The contributions are stated at the formulation, method, and evaluation levels.
Quantitative comparative claims are restricted to results obtained under the
corresponding frozen protocol and held-out evaluation.

\section{Thesis Organization}
\label{sec:introduction-organization}

The remainder of this thesis is organized as follows. Chapter~\ref{ch:background}
reviews vehicular beam management, sensing-aided beam prediction, ISAC
predictive beamforming, BEV and cooperative perception, and sensing
target-to-user association. It uses these research strands to identify the need
for broad, condition-resilient sensing and identity-consistent beam alignment.

Chapter~\ref{ch:system-model} defines the target-BS local coordinate system,
the multimodal observations, the physical-target, perception-track, and
communication-UE identities, the sensing target-to-user correspondence, and the
codebook, candidate-measurement, and resource models. Chapter~\ref{ch:methodology}
then presents the proposed framework, including cross-node BEV fusion, joint
detection and beam-quality learning, multi-object correspondence maintenance,
measurement-assisted association, reliability-gated candidate scanning, and the
communication interface.

Chapter~\ref{ch:experiments} describes the data protocol, comparison methods,
layered metrics, and system-level evaluation. It examines how multimodal and
cross-node complementarity, sensing target-to-user association, and candidate
measurement decisions affect communication performance under common resource
assumptions. Finally, Chapter~\ref{ch:conclusion} summarizes the findings
supported by the evaluation, discusses the limitations of the local BS scope and
communication abstraction, and outlines extensions toward cross-BS
correspondence, measurement calibration, and more detailed protocol-level
assessment.
