\chapter{Proposed Sensing-Assisted Beam Management Framework}
\label{ch:methodology}

This chapter specifies the proposed sensing-assisted beam-management framework
under the system model of Chapter~\ref{ch:system-model}.  The framework is
organised around a strict separation between a physical vehicle observed by the
sensing system and a VUE addressed by the communication system.  Multimodal
sensing first produces target-level evidence in a target-BS-centred BEV
representation.  Conventional communication measurements then establish the
target-to-user association required to use that evidence, and CSI-RS candidate
reduction is permitted only while this association is both reliable and
supported by a current observation.  Sensing therefore ranks measurements; it
does not replace CSI-RS-based service-beam selection.

The proposed method comprises four coupled functions: distributed multimodal
BEV perception and beam-quality learning, IMM-based multi-object tracking,
measurement-assisted target-to-user association, and reliability-aware
candidate selection.  The first two functions operate in the sensing domain and
retain unbound physical-target evidence.  The latter two use conventional beam
measurements to connect that evidence to an NR-oriented beam-management
procedure.  The resource model and system-level evaluation of this procedure
are specified in Chapter~\ref{ch:experiments}.

\section{Framework Architecture}
\label{sec:method-framework}

For each target BS \(b\) and sensing epoch \(n\), the framework follows four
ordered stages.  The first two stages run on the sensing time line and produce
temporally coherent evidence for physical vehicles.  The remaining stages are
invoked when this evidence must support a VUE-specific measurement decision.
This ordering makes explicit how an unbound sensing target can assist beam
management without being treated as an already identified VUE.

\begin{enumerate}
    \item \emph{Distributed multimodal perception and beam-quality
    prediction.}  The network processes \(\mathcal{O}_{b,n}\), defined in
    Section~\ref{sec:system-sensing}, in a target-BS-centred BEV frame.  It
    outputs a set of unbound vehicle detections
    \(\{(d_{b,i,n},\mathbf{p}_{b,i,n})\}_i\).  Each \(d_{b,i,n}\) contains a
    BEV position, available attributes, and detection confidence, while
    \(\mathbf{p}_{b,i,n}\) is a normalised 192-way CSI beam-quality
    distribution.  The distribution ranks beams that are promising to measure
    for that physical target; it is neither a VUE identifier nor a service-beam
    decision.

    \item \emph{IMM-based multi-object tracking.}  The CV and CT branches of
    the IMM predict the motion of each physical target and update their model
    probabilities from the current BEV detection.  Innovation gating and
    one-to-one detection--track assignment associate current observations with
    predicted tracks.  The resulting track set \(\mathcal{R}_{b,n}\) maintains
    target position, motion state, uncertainty, confidence, observation
    history, and the current beam-quality distribution.  It establishes sensing
    continuity only: a perception track remains distinct from a communication
    UE.

    \item \emph{Initial or renewed target-to-user association.}  At initial
    access, after a serving-cell change, or when an existing binding loses
    support, conventional SSB and CSI-RS measurements provide VUE-indexed beam
    evidence.  The measured CSI-RS beam of each affected VUE is evaluated under
    the beam-quality distributions of currently observed tracks.  SSB-parent
    consistency first excludes infeasible pairs; a one-to-one assignment with
    an unmatched alternative then determines whether the measurement evidence
    supports an accepted UE--track mapping \(\pi_{b,n}\).  Ambiguous pairs
    remain unbound rather than being forced to a sensing target.

    \item \emph{Reliability-aware candidate selection.}  An accepted mapping
    is used only when its track is currently observed and its binding,
    detection, and beam-distribution evidence jointly support candidate use.
    The corresponding current distribution then defines a fixed or adaptive
    CSI-RS candidate set.  Otherwise, conventional refinement is retained.
    In either case, the service beam is chosen only after CSI-RS quality has
    been measured over the selected candidate set.
\end{enumerate}

The resulting information flow is concisely represented by
\begin{equation}
    \mathcal{O}_{b,n}
    \longrightarrow
    \bigl\{d_{b,i,n},\mathbf{p}_{b,i,n}\bigr\}_{i}
    \longrightarrow
    \mathcal{R}_{b,n}
    \longrightarrow
    \pi_{b,n}
    \longrightarrow
    \mathcal{C}_{b,u,n},
    \label{eq:method-decision-path}
\end{equation}
where \(\mathcal{R}_{b,n}\) is the set of perception tracks,
\(\pi_{b,n}\) denotes the partial mapping formed from accepted UE--track
associations, and \(\mathcal{C}_{b,u,n}\) is either a sensing-derived CSI-RS
candidate set or a conventional refinement set.  This sequence provides the
logical structure for the overview figure; Sections~\ref{sec:method-perception-learning},
\ref{sec:method-imm-tracking}, and \ref{sec:method-measurement-association}
develop the corresponding models.

Four information boundaries define the decision path.  First, the perception
network receives calibrated camera and point-cloud observations only; link
coordinates, VUE identities, and oracle beam labels are excluded from its
forward input.  Second, the IMM propagates BEV target states and uncertainty,
not communication identities.  Third, initial or renewed association uses
conventional SSB/CSI-RS evidence together with predicted beam likelihoods,
without ground-truth IDs or a geometric inversion from position to beam index.
Finally, a sensing distribution may reduce CSI-RS measurements only for a
currently observed, reliable association; the measured CSI-RS quality, rather
than the neural prediction, selects the service beam.  These boundaries make
the distinct consequences of perception, tracking, association, and candidate
reduction identifiable in the evaluation.

\section{Distributed Multimodal BEV Perception and Beam-Quality Learning}
\label{sec:method-perception-learning}

This section develops the perception-and-learning pipeline that implements the
first stage of the framework.  It first constructs a target-BS-centred BEV
representation from distributed visual observations and BS-local ISAC sensing,
then decodes vehicle-level outputs and their beam-quality distributions from
the shared representation.  The final subsection specifies the distributional
supervision that makes these outputs suitable for candidate ranking rather than
for direct service-beam declaration.

\subsection{Multimodal BEV Representation}
\label{subsec:method-bev-representation}

The BEV representation provides a common spatial interface for distributed
visual observations, BS-local ISAC sensing, vehicle detection, and beam-quality
learning.  Let \(\mathcal{J}_b=\{b\}\cup\mathcal{N}_b\) denote the target BS
and its neighbouring SNs.  For each node \(j\in\mathcal{J}_b\), calibrated
multiview images are encoded and lifted into the BEV frame of BS \(b\):
\begin{equation}
    \mathbf{F}^{\mathrm{cam}}_{j\rightarrow b,n}
    =
    \Phi_{\mathrm{img}}\!
    \left(
    \mathcal{I}_{j,n};\mathbf{T}_{j\rightarrow b}
    \right),
    \label{eq:method-camera-lift}
\end{equation}
where \(\mathbf{T}_{j\rightarrow b}\) denotes the calibration information that
expresses node \(j\)'s visual evidence in the target-BS-centred coordinate
system.  The representation requires that all node features be expressed in
these common BEV coordinates before aggregation, independent of the particular
image encoder or view-transformation implementation.

The distributed visual evidence is aggregated as
\begin{equation}
    \mathbf{F}^{\mathrm{cam}}_{b,n}
    =
    \Phi_{\mathrm{node}}
    \left(
    \left\{
    \mathbf{F}^{\mathrm{cam}}_{j\rightarrow b,n},
    \mathbf{m}^{\mathrm{cam}}_{j,n}
    \right\}_{j\in\mathcal{J}_b}
    \right),
    \label{eq:method-node-aggregation}
\end{equation}
where \(\mathbf{m}^{\mathrm{cam}}_{j,n}\) captures view availability or
reliability.  The study compares node aggregation mechanisms, including uniform
aggregation and learned cross-node attention, within the common operator
\(\Phi_{\mathrm{node}}\).  Across these mechanisms, neighbouring nodes serve the
same algorithmic purpose: they supplement the target-BS view when its coverage
is incomplete or affected by occlusion.

The BS-local ISAC point cloud is independently encoded on the same grid,
\begin{equation}
    \mathbf{F}^{\mathrm{isac}}_{b,n}
    =
    \Phi_{\mathrm{pc}}\!
    \left(\mathcal{P}_{b,n}\right).
    \label{eq:method-isac-encoding}
\end{equation}
The camera and point-cloud representations are combined by a modality-fusion
operator,
\begin{equation}
    \mathbf{F}_{b,n}
    =
    \Phi_{\mathrm{modal}}
    \left(
    \mathbf{F}^{\mathrm{cam}}_{b,n},
    \mathbf{F}^{\mathrm{isac}}_{b,n};
    \mathbf{m}^{\mathrm{modal}}_{b,n}
    \right),
    \label{eq:method-modal-fusion}
\end{equation}
where \(\mathbf{m}^{\mathrm{modal}}_{b,n}\) represents modality availability or
confidence.  Modality gating can downweight unreliable evidence, while node
aggregation preserves complementary visual observations.  Neither operation is
used to infer a communication identity; their role is to construct a
target-level scene representation with improved observability.

The shared BEV representation aligns a detected vehicle and its beam-quality
supervision with the local service region of BS \(b\).  It also enables
cross-view evidence to influence both detection and beam-quality prediction
before target-level outputs are decoded.  The resulting feature map
\(\mathbf{F}_{b,n}\) is therefore shared by the two prediction tasks described
next.

\subsection{Joint Detection and Beam-Quality Prediction}
\label{subsec:method-target-prediction}

The joint prediction head maps \(\mathbf{F}_{b,n}\) to a vehicle-centre
heatmap, target attributes, and a spatially dense CSI beam-quality map:
\begin{equation}
    \left(
    \mathbf{H}_{b,n},
    \mathbf{A}_{b,n},
    \mathbf{P}_{b,n}
    \right)
    =
    \Phi_{\mathrm{joint}}\!
    \left(\mathbf{F}_{b,n}\right),
    \label{eq:method-joint-head}
\end{equation}
where \(\mathbf{H}_{b,n}\) is the centre heatmap, \(\mathbf{A}_{b,n}\)
contains geometric or motion-related attributes, and
\(\mathbf{P}_{b,n}\) contains \(M_{\mathrm{CSI}}=192\) beam scores at every BEV
location.  Local maxima of \(\mathbf{H}_{b,n}\) define the vehicle centres.  At
the \(i\)-th decoded centre, the target-level output is
\begin{equation}
    d_{b,i,n}
    =
    \left(
    \widehat{\mathbf{r}}_{b,i,n},
    \widehat{\mathbf{a}}_{b,i,n},
    \widehat{c}_{b,i,n}
    \right),\qquad
    \mathbf{p}_{b,i,n}
    =
    \operatorname{Sample}
    \left(
    \mathbf{P}_{b,n},
    \widehat{\mathbf{r}}_{b,i,n}
    \right).
    \label{eq:method-target-output}
\end{equation}
Here, \(\widehat{\mathbf{r}}_{b,i,n}\) is the estimated BEV centre,
\(\widehat{\mathbf{a}}_{b,i,n}\) contains available size, heading, and velocity
attributes, and \(\widehat{c}_{b,i,n}\) is the detection confidence.  Sampling
\(\mathbf{P}_{b,n}\) at the decoded centre converts the dense map into a
distribution specific to the corresponding physical target.  Consequently,
several simultaneously visible vehicles can receive distinct candidate rankings
from a single shared BEV representation.

During training, the BS--UE link coordinate identifies the BEV location at
which beam supervision is sampled.  It acts solely as a supervision index: it
is excluded from the forward model and is not inverted to obtain a beam index at
inference time.  The prediction head also receives neither the VUE identity nor
an oracle track identity.  Equation~\eqref{eq:method-target-output} therefore
defines an unbound target-level output that remains suitable for the subsequent
association stage.

\subsection{Distributional Beam Supervision}
\label{subsec:method-distributional-supervision}

For a supervised BS--UE link, let \(g_{b,u,n}(k)\) be the CSI beam quality in
Equation~\eqref{eq:system-beam-quality}.  The physical power vector is
converted to a soft target distribution,
\begin{equation}
    q_{b,u,n}(k)
    =
    \operatorname{softmax}\!\left(
    \frac{
    10\log_{10}g_{b,u,n}(k)
    -
    \max_j 10\log_{10}g_{b,u,n}(j)}
    {T}
    \right),
    \qquad
    k=1,\ldots,M_{\mathrm{CSI}},
    \label{eq:method-soft-beam-target}
\end{equation}
where \(T\) controls the concentration of the target distribution.  In contrast
to a strongest-beam label, \(q_{b,u,n}\) preserves the relative usefulness of
multiple beams.  This information is required by CSI-RS candidate selection,
for which a predicted list can be useful even when its leading entry is not the
unique strongest physical beam.

Let \(\mathbf{z}_{b,i,n}\) be the unnormalised prediction logits at a supervised
target location, and let
\(\mathbf{p}_{b,i,n}=\operatorname{softmax}(\mathbf{z}_{b,i,n})\).  The beam
loss is
\begin{equation}
    \mathcal{L}_{\mathrm{beam}}
    =
    D_{\mathrm{KL}}
    \left(
    \mathbf{q}_{b,u,n}\Vert\mathbf{p}_{b,i,n}
    \right)
    +
    \lambda_{\mathrm{rank}}
    \mathcal{L}_{\mathrm{hard-rank}}.
    \label{eq:method-beam-loss}
\end{equation}
The first term matches the predicted and physical quality distributions.  The
second penalises ranking violations between the strongest physical beam and a
set \(\mathcal{H}^{-}_{b,u,n}\) of substantially weaker hard-negative beams:
\begin{equation}
    \mathcal{L}_{\mathrm{hard-rank}}
    =
    \frac{1}{|\mathcal{H}^{-}_{b,u,n}|}
    \sum_{k\in\mathcal{H}^{-}_{b,u,n}}
    \ell_{\mathrm{rank}}
    \left(
    z_{b,i,n}(k^\star_{b,u,n}),
    z_{b,i,n}(k)
    \right),
    \label{eq:method-hard-rank-loss}
\end{equation}
where \(k^\star_{b,u,n}\) is the strongest physical CSI beam and
\(\ell_{\mathrm{rank}}(\cdot,\cdot)\) is a pairwise ranking penalty.  The
ranking term suppresses score inversions in which a substantially weaker beam
outranks the strongest beam in the exported candidate list.

The complete training objective combines the detection and beam terms,
\begin{equation}
    \mathcal{L}_{\mathrm{joint}}
    =
    \lambda_{\mathrm{hm}}\mathcal{L}_{\mathrm{hm}}
    +
    \lambda_{\mathrm{attr}}\mathcal{L}_{\mathrm{attr}}
    +
    \lambda_{\mathrm{beam}}\mathcal{L}_{\mathrm{beam}},
    \label{eq:method-joint-loss}
\end{equation}
where \(\mathcal{L}_{\mathrm{hm}}\) and
\(\mathcal{L}_{\mathrm{attr}}\) supervise the vehicle-centre and target-attribute
outputs, respectively.  The objective learns a calibrated, candidate-oriented
quality distribution rather than an unmeasured service-beam decision.  Its
effect is assessed through detection-conditioned beam ranking, power retention,
and calibration metrics.

Three list lengths serve distinct functions.  The model exports the full
\(K_{\mathrm{model}}=M_{\mathrm{CSI}}\)-entry distribution.  Association may
inspect a ranked subset of length \(K_{\mathrm{bind}}\), whereas CSI-RS measures
only \(K_{\mathrm{scan}}\) beams after a binding is accepted.  Preserving this
distinction prevents an information-rich prediction from being interpreted as
an equally large measurement budget.

\section{IMM-Based Multi-Object Tracking}
\label{sec:method-imm-tracking}

The perception network produces an unbound detection whenever a vehicle is
visible, but a beam hint also requires temporal continuity when vehicles move,
turn, or are intermittently observed.  This section therefore estimates the
state of physical targets only.  Each target BS maintains an independent track
set for each data split and weather condition; a track is neither a recognised
VUE nor a cross-cell identity.  The interacting multiple model (IMM) filter
combines a constant-velocity (CV) hypothesis with a coordinated-turn (CT)
hypothesis, allowing the motion estimate to adapt to the local vehicle
trajectory.

\subsection{Motion Models}
\label{subsec:method-motion-models}

For the CV model, the state of track \(r\) is represented in Cartesian BEV
coordinates as
\begin{equation}
    \mathbf{x}^{\mathrm{CV}}_{r,n}
    =
    [x_{r,n},y_{r,n},v_{x,r,n},v_{y,r,n}]^{\mathsf T}.
    \label{eq:method-cv-state}
\end{equation}
With sensing interval \(\Delta t\), its linear process and position-measurement
models are
\begin{equation}
    \mathbf{x}^{\mathrm{CV}}_{r,n}
    =
    \mathbf{F}_{\mathrm{CV}}\mathbf{x}^{\mathrm{CV}}_{r,n-1}
    +\mathbf{w}^{\mathrm{CV}}_{r,n},
    \qquad
    \mathbf{z}_{i,n}
    =
    \mathbf{H}_{\mathrm{CV}}\mathbf{x}^{\mathrm{CV}}_{r,n}
    +\mathbf{v}_{i,n},
    \label{eq:method-cv-model}
\end{equation}
where
\begin{equation}
    \mathbf{F}_{\mathrm{CV}}
    =
    \begin{bmatrix}
        1&0&\Delta t&0\\
        0&1&0&\Delta t\\
        0&0&1&0\\
        0&0&0&1
    \end{bmatrix},
    \qquad
    \mathbf{H}_{\mathrm{CV}}
    =
    \begin{bmatrix}
        1&0&0&0\\
        0&1&0&0
    \end{bmatrix}.
    \label{eq:method-cv-matrices}
\end{equation}
Here, \(\mathbf{z}_{i,n}=[\widehat{x}_{b,i,n},\widehat{y}_{b,i,n}]^{\mathsf T}\)
is the BEV centre of detection \(d_{b,i,n}\), and
\(\mathbf{w}^{\mathrm{CV}}_{r,n}\sim\mathcal{N}(\mathbf{0},\mathbf{Q}_{\mathrm{CV}})\)
and \(\mathbf{v}_{i,n}\sim\mathcal{N}(\mathbf{0},\mathbf{R}_{i,n})\) represent
process and detection uncertainty.  The CV model is appropriate when target
motion is locally close to rectilinear.  In particular, the observation model
is defined by the BEV detection interface of the present framework; it is not
identified with the measurement model of a radar- or communication-based
tracker.

The CT model uses the speed--heading representation
\begin{equation}
    \mathbf{x}^{\mathrm{CT}}_{r,n}
    =
    [x_{r,n},y_{r,n},v_{r,n},\psi_{r,n},\omega_{r,n}]^{\mathsf T},
    \label{eq:method-ct-state}
\end{equation}
where \(v_{r,n}\), \(\psi_{r,n}\), and \(\omega_{r,n}\) denote speed, heading,
and turn rate.  For \(|\omega_{r,n-1}|>0\), the coordinated-turn state evolution
is
\begin{equation}
    \mathbf{x}^{\mathrm{CT}}_{r,n}
    =
    \begin{bmatrix}
        x_{r,n-1}+\dfrac{v_{r,n-1}}{\omega_{r,n-1}}
        \left[\sin(\psi_{r,n-1}+\omega_{r,n-1}\Delta t)-\sin\psi_{r,n-1}\right]\\[3pt]
        y_{r,n-1}+\dfrac{v_{r,n-1}}{\omega_{r,n-1}}
        \left[\cos\psi_{r,n-1}-\cos(\psi_{r,n-1}+\omega_{r,n-1}\Delta t)\right]\\[3pt]
        v_{r,n-1}\\
        \psi_{r,n-1}+\omega_{r,n-1}\Delta t\\
        \omega_{r,n-1}
    \end{bmatrix}
    +\mathbf{w}^{\mathrm{CT}}_{r,n}
    \triangleq
    f_{\mathrm{CT}}\!\left(\mathbf{x}^{\mathrm{CT}}_{r,n-1}\right)
    +\mathbf{w}^{\mathrm{CT}}_{r,n}.
    \label{eq:method-ct-model}
\end{equation}
The zero-turn-rate limit gives
\(x_{r,n}=x_{r,n-1}+v_{r,n-1}\Delta t\cos\psi_{r,n-1}\) and
\(y_{r,n}=y_{r,n-1}+v_{r,n-1}\Delta t\sin\psi_{r,n-1}\), recovering local
straight-line motion without a numerical singularity.  The CT measurement
function extracts position, \(h_{\mathrm{CT}}(\mathbf{x})=[x,y]^{\mathsf T}\),
and its EKF transition and measurement matrices are the corresponding Jacobians
\(\mathbf{F}_{\mathrm{CT}}=\partial f_{\mathrm{CT}}/\partial\mathbf{x}\) and
\(\mathbf{H}_{\mathrm{CT}}=\partial h_{\mathrm{CT}}/\partial\mathbf{x}\),
evaluated at the predicted state.  Thus, the CT kinematics describe vehicle
motion, whereas the update remains conditioned on the position observations
and effective detection uncertainty produced by the multimodal BEV detector.

The two model states use different coordinates.  Let
\(\mathcal{T}_{q\rightarrow \ell}(\cdot)\) denote the deterministic conversion
between their Cartesian and speed--heading forms, and let
\(\mathbf{J}_{q\rightarrow \ell}\) be its Jacobian.  These transformations are
applied whenever states or covariances are exchanged between models, allowing
the IMM to retain a consistent uncertainty representation.
In particular, the state components are converted according to
\begin{equation}
    \mathcal{T}_{\mathrm{CV}\rightarrow\mathrm{CT}}
    \left([x,y,v_x,v_y]^{\mathsf T}\right)
    =
    [x,y,\sqrt{v_x^2+v_y^2},\operatorname{atan2}(v_y,v_x),0]^{\mathsf T},
    \label{eq:method-cv-to-ct}
\end{equation}
and
\begin{equation}
    \mathcal{T}_{\mathrm{CT}\rightarrow\mathrm{CV}}
    \left([x,y,v,\psi,\omega]^{\mathsf T}\right)
    =
    [x,y,v\cos\psi,v\sin\psi]^{\mathsf T}.
    \label{eq:method-ct-to-cv}
\end{equation}
The corresponding Jacobians propagate covariance through these transformations;
the zero turn-rate component in the CV-to-CT conversion expresses the absence
of turn-rate information in the CV state rather than a permanent motion
constraint.

\subsection{IMM Filtering and Track Management}
\label{subsec:method-imm-filtering}

Let \(\mathcal{Q}=\{\mathrm{CV},\mathrm{CT}\}\) be the set of motion models and
\(\pi_{q\ell}=\Pr(m_n=\ell\mid m_{n-1}=q)\) the Markov transition probability
from model \(q\) to model \(\ell\).  Given posterior mode probabilities
\(\mu^{(q)}_{r,n-1}\), the predicted probability and mixing probability for
model \(\ell\) are
\begin{equation}
    \bar{\mu}^{(\ell)}_{r,n}
    =
    \sum_{q\in\mathcal{Q}}\pi_{q\ell}\mu^{(q)}_{r,n-1},
    \qquad
    \mu^{(q\mid\ell)}_{r,n-1}
    =
    \frac{\pi_{q\ell}\mu^{(q)}_{r,n-1}}
    {\bar{\mu}^{(\ell)}_{r,n}}.
    \label{eq:method-imm-mixing-probability}
\end{equation}
The state and covariance supplied to model \(\ell\) are consequently
\begin{align}
    \widehat{\mathbf{x}}^{(\ell)}_{r,0,n-1}
    &=
    \sum_{q\in\mathcal{Q}}
    \mu^{(q\mid\ell)}_{r,n-1}
    \mathcal{T}_{q\rightarrow\ell}
    \left(\widehat{\mathbf{x}}^{(q)}_{r,n-1}\right),
    \label{eq:method-imm-mixed-state}\\
    \mathbf{P}^{(\ell)}_{r,0,n-1}
    &=
    \sum_{q\in\mathcal{Q}}
    \mu^{(q\mid\ell)}_{r,n-1}
    \left[
    \mathbf{J}_{q\rightarrow\ell}\mathbf{P}^{(q)}_{r,n-1}
    \mathbf{J}_{q\rightarrow\ell}^{\mathsf T}
    +\mathbf{e}^{(q,\ell)}_{r,n-1}
    \left(\mathbf{e}^{(q,\ell)}_{r,n-1}\right)^{\mathsf T}
    \right],
    \label{eq:method-imm-mixed-covariance}
\end{align}
where \(\mathbf{e}^{(q,\ell)}_{r,n-1}\) is the difference between the
transformed state of mode \(q\) and the mixed state of mode \(\ell\).

Each mixed state is propagated and corrected by its model-conditioned filter.
With \(f_{\ell}\) denoting either the CV or CT transition, the filtering
recursion is
\begin{align}
    \widehat{\mathbf{x}}^{(\ell)-}_{r,n}
    &=f_{\ell}\!\left(\widehat{\mathbf{x}}^{(\ell)}_{r,0,n-1}\right),
    \label{eq:method-imm-prediction}\\
    \mathbf{P}^{(\ell)-}_{r,n}
    &=\mathbf{F}_{\ell}\mathbf{P}^{(\ell)}_{r,0,n-1}
    \mathbf{F}_{\ell}^{\mathsf T}+\mathbf{Q}_{\ell},\\
    \boldsymbol{\nu}^{(\ell)}_{r,i,n}
    &=\mathbf{z}_{i,n}-h_{\ell}\!\left(\widehat{\mathbf{x}}^{(\ell)-}_{r,n}\right),
    \label{eq:method-imm-innovation}\\
    \mathbf{S}^{(\ell)}_{r,i,n}
    &=\mathbf{H}_{\ell}\mathbf{P}^{(\ell)-}_{r,n}
    \mathbf{H}_{\ell}^{\mathsf T}+\mathbf{R}_{i,n},\\
    \mathbf{K}^{(\ell)}_{r,i,n}
    &=\mathbf{P}^{(\ell)-}_{r,n}\mathbf{H}_{\ell}^{\mathsf T}
    \left(\mathbf{S}^{(\ell)}_{r,i,n}\right)^{-1},\\
    \widehat{\mathbf{x}}^{(\ell)}_{r,n}
    &=\widehat{\mathbf{x}}^{(\ell)-}_{r,n}
    +\mathbf{K}^{(\ell)}_{r,i,n}\boldsymbol{\nu}^{(\ell)}_{r,i,n},
    \label{eq:method-imm-state-update}\\
    \mathbf{P}^{(\ell)}_{r,n}
    &=(\mathbf{I}-\mathbf{K}^{(\ell)}_{r,i,n}\mathbf{H}_{\ell})
    \mathbf{P}^{(\ell)-}_{r,n}
    (\mathbf{I}-\mathbf{K}^{(\ell)}_{r,i,n}\mathbf{H}_{\ell})^{\mathsf T}
    +\mathbf{K}^{(\ell)}_{r,i,n}\mathbf{R}_{i,n}
    \left(\mathbf{K}^{(\ell)}_{r,i,n}\right)^{\mathsf T}.
    \label{eq:method-imm-covariance-update}
\end{align}
For the CV branch, \(\mathbf{F}_{\ell}\) and \(\mathbf{H}_{\ell}\) are the
linear matrices in Equation~\eqref{eq:method-cv-matrices}; for the CT branch,
they are the EKF Jacobians.  The innovation likelihood updates the model weight:
\begin{equation}
    \Lambda^{(\ell)}_{r,i,n}
    =
    \frac{\exp\!\left[-\tfrac{1}{2}
    \boldsymbol{\nu}^{(\ell)\mathsf T}_{r,i,n}
    \left(\mathbf{S}^{(\ell)}_{r,i,n}\right)^{-1}
    \boldsymbol{\nu}^{(\ell)}_{r,i,n}\right]}
    {\sqrt{(2\pi)^2\left|\mathbf{S}^{(\ell)}_{r,i,n}\right|}},
    \qquad
    \mu^{(\ell)}_{r,n}
    =
    \frac{\Lambda^{(\ell)}_{r,i,n}\bar{\mu}^{(\ell)}_{r,n}}
    {\sum_{j\in\mathcal{Q}}
    \Lambda^{(j)}_{r,i,n}\bar{\mu}^{(j)}_{r,n}}.
    \label{eq:method-imm-mode-update}
\end{equation}
Let \(\mathcal{T}_{\ell\rightarrow\mathrm{c}}\) map a mode-conditioned estimate
to a common output coordinate.  The IMM estimate is obtained by moment matching:
\begin{align}
    \widehat{\mathbf{x}}_{r,n}
    &=
    \sum_{\ell\in\mathcal{Q}}
    \mu^{(\ell)}_{r,n}
    \mathcal{T}_{\ell\rightarrow\mathrm{c}}
    \left(\widehat{\mathbf{x}}^{(\ell)}_{r,n}\right),
    \label{eq:method-imm-fused-state}\\
    \mathbf{P}_{r,n}
    &=
    \sum_{\ell\in\mathcal{Q}}
    \mu^{(\ell)}_{r,n}
    \left[
    \mathbf{J}_{\ell\rightarrow\mathrm{c}}
    \mathbf{P}^{(\ell)}_{r,n}
    \mathbf{J}_{\ell\rightarrow\mathrm{c}}^{\mathsf T}
    +\boldsymbol{\delta}^{(\ell)}_{r,n}
    \left(\boldsymbol{\delta}^{(\ell)}_{r,n}\right)^{\mathsf T}
    \right],
    \label{eq:method-imm-fused-covariance}
\end{align}
where \(\boldsymbol{\delta}^{(\ell)}_{r,n}\) is the displacement between the
transformed mode-conditioned estimate and the fused state.  IMM thus adjusts the
relative weight of straight and turning motion from the current innovation,
rather than permanently assigning a vehicle to either model.

Before an update, predicted tracks and current detections are screened by the
squared Mahalanobis innovation distance
\begin{equation}
    D^2_{r,i,n}
    =
    \left(\mathbf{z}_{i,n}-\widehat{\mathbf{z}}_{r,n|n-1}\right)^{\mathsf T}
    \mathbf{S}^{-1}_{r,n}
    \left(\mathbf{z}_{i,n}-\widehat{\mathbf{z}}_{r,n|n-1}\right)
    \leq \gamma_{\mathrm{trk}}.
    \label{eq:method-track-gate}
\end{equation}
The surviving pairs are resolved by one-to-one Hungarian assignment using their
innovation costs.  A matched detection updates the kinematic state, mode
probabilities, track confidence, observation history, and current beam-quality
distribution \(\mathbf{p}^{\mathrm{obs}}_{r,n}\).  An unmatched track can be
retained temporarily, but its predicted location alone never produces a formal
beam candidate.  Tracking consequently maintains temporal continuity without
substituting for a communication measurement or target-to-user association.

\section{Measurement-Assisted Target-to-User Association}
\label{sec:method-measurement-association}

The distribution learned in Section~\ref{sec:method-perception-learning} is indexed by a currently observed physical track, whereas beam management acts on a VUE.  This section uses conventional beam measurements to bridge the two indices.  It first establishes a partial UE--track mapping in a multi-candidate scene and then determines whether the accepted mapping is sufficiently reliable to reduce the CSI-RS measurement set.

\subsection{Initial Association from Beam Measurements}
\label{subsec:method-beam-measurement-association}

An association event occurs at initial access, after a serving-cell change, or when an existing binding no longer has adequate support.  The conventional SSB and CSI-RS procedure provides the serving SSB \(s_{b,u,n}\) and a VUE-indexed CSI-RS beam measurement \(\kappa_{b,u,n}\) for every affected VUE \(u\).  In contrast, a currently observed track \(r\) provides the normalised beam-quality distribution \(\mathbf{p}^{\mathrm{obs}}_{r,n}\) from the joint perception network.  Its entry \(p^{\mathrm{obs}}_{r,n}(k)\) is interpreted as the relative compatibility of beam \(k\) with the physical target represented by track \(r\).

The compatibility between a VUE measurement and a track is quantified by the normalised negative log likelihood
\begin{equation}
    c^{\mathrm{bind}}_{u,r,n}
    =
    -\frac{\log\!\left(p^{\mathrm{obs}}_{r,n}\bigl(\kappa_{b,u,n}\bigr)+\epsilon\right)}{\log M_{\mathrm{CSI}}},
    \label{eq:method-binding-cost}
\end{equation}
where \(\epsilon>0\) is a numerical constant.  A smaller value means that the beam selected by conventional measurement is assigned higher quality by the track-level prediction.  This converts the distributional output of the beam-quality-learning task into a communication-grounded association score, without requiring the perception network to classify a VUE identity.

The parent relation between CSI-RS and SSB beams and the current-observation requirement define the feasible edge set
\begin{equation}
    \mathcal{E}^{\mathrm{bind}}_{b,n}
    =
    \left\{(u,r):\varphi_b\bigl(\kappa_{b,u,n}\bigr)=s_{b,u,n},\ r\ \text{is currently observed}\right\}.
    \label{eq:method-binding-feasibility}
\end{equation}
Let \(\sigma\) assign each affected VUE either to one feasible track or to a dummy unmatched column with cost \(c_{\emptyset}\).  The one-to-one association is obtained from
\begin{equation}
    \widehat{\sigma}
    =
    \underset{\sigma}{\arg\min}
    \sum_{u\in\mathcal{U}^{\mathrm{evt}}_b[n]}c^{\mathrm{bind}}_{u,\sigma(u),n},
    \qquad
    \sigma(u)\in\mathcal{R}^{\mathrm{obs}}_{b,n}\cup\{\emptyset\},
    \label{eq:method-binding-assignment}
\end{equation}
subject to the feasible edges and the one-to-one constraint on real tracks.  It is solved by the Hungarian algorithm after augmentation with dummy columns.  For a real assigned pair, let \(\Delta_{u,r,n}\) denote the gap between its cost and the best competing feasible cost.  The binding is accepted only when
\begin{equation}
    A_{u,r,n}
    =
    \mathbf{1}\!\left\{c^{\mathrm{bind}}_{u,r,n}\leq\tau_{\mathrm{bind}},\ \Delta_{u,r,n}\geq\tau_{\mathrm{margin}}\right\}=1.
    \label{eq:method-binding-acceptance}
\end{equation}
Accordingly, \(\pi_{b,n}(u)=r\) for an accepted pair and \(\pi_{b,n}(u)=\varnothing\) otherwise.  The unmatched option is essential: it prevents an ambiguous multi-candidate scene from forcing a sensing target onto the wrong communication user.

The association procedure excludes ground-truth identities and never maps a predicted BEV position directly to a codebook beam.  Direction-only and Top-\(K\)-membership rules are retained as association ablations; the proposed rule instead uses agreement between a learned beam-quality distribution and a VUE-indexed conventional measurement.  Once accepted, a binding follows the corresponding perception track and is reassessed when the supporting sensing or communication evidence changes.

\subsection{Reliability-Aware Candidate Selection}
\label{subsec:method-reliability-aware-selection}

An accepted binding is necessary but insufficient for reducing CSI-RS measurements.  Let \(G_{u,n}\in\{0,1\}\) denote the candidate-use decision for VUE \(u\).  It combines the accepted binding with non-ground-truth evidence available at the BS,
\begin{equation}
    G_{u,n}
    =
    \begin{cases}
        \Gamma\!\left(\boldsymbol{\xi}_{u,n}\right),&
        \pi_{b,n}(u)=r\in\mathcal{R}^{\mathrm{obs}}_{b,n}\ \text{and}\ A_{u,r,n}=1,\\
        0,& \text{otherwise},
    \end{cases}
    \label{eq:method-reliability-gate}
\end{equation}
where \(\boldsymbol{\xi}_{u,n}\) includes binding confidence, assignment margin, current detection and track confidence, hint age, SSB-parent consistency, observation history, and beam-score concentration.  The function \(\Gamma(\cdot)\) represents a calibrated threshold rule.  It separates association correctness from the more conservative question of whether the current sensing hint is suitable for candidate reduction.

When \(G_{u,n}=1\), the current observation refreshes the track distribution and supplies a sensing-assisted candidate set; otherwise conventional refinement remains active:
\begin{equation}
    \mathcal{C}_{b,u,n}
    =
    \begin{cases}
        \operatorname{TopK}_{K_{\mathrm{scan}}}\left(\mathbf{p}^{\mathrm{obs}}_{\pi_{b,n}(u),n}\right),& G_{u,n}=1,\\
        \mathcal{C}^{\mathrm{conv}}_{b,u,n},& G_{u,n}=0.
    \end{cases}
    \label{eq:method-candidate-policy}
\end{equation}
Thus, a predicted-only track can preserve state-estimation continuity but cannot alone initiate a reduced CSI-RS scan.

The measurement width can adapt to the concentration of the current distribution.  Let \(s_1\geq\cdots\geq s_{K_{\max}}\) be its leading scores.  For minimum width \(K_{\min}\) and score-mass target \(\zeta\), the selected width is
\begin{equation}
    K^{\star}_{\mathrm{scan}}
    =
    \min\left\{k:k\geq K_{\min},\ \frac{\sum_{j=1}^{k}s_j}{\sum_{j=1}^{K_{\max}}s_j}\geq\zeta\right\}.
    \label{eq:method-adaptive-scan}
\end{equation}
Diffuse distributions consequently retain more CSI-RS candidates, whereas concentrated distributions permit a narrower scan.  In both cases, the distribution determines only which beams are measured.  The service beam is selected from the measured candidate set according to Equation~\eqref{eq:system-service-beam}; a rejected hint reverts to conventional refinement and provides a recovery path.

This association-to-candidate interface prevents association errors, missed detections, and stale target evidence from directly constraining a VUE's measurement set.  Its system consequences are evaluated jointly through association coverage, hint usage, fallback frequency, candidate recall, CSI-RS overhead, and post-RZF rate.

\section{Algorithm Summary and Complexity}
\label{sec:method-algorithm}

Algorithm~\ref{alg:method-framework} summarises the procedure at a target BS.
It distinguishes association events from ordinary maintenance epochs.
Association events use conventional measurements to establish or recover a
VUE--track mapping; maintenance epochs retain that mapping only when current
sensing evidence and the reliability gate support it.

\begin{algorithm}[t]
\caption{Measurement-assisted sensing beam management at target BS \(b\)}
\label{alg:method-framework}
\begin{algorithmic}[1]
\REQUIRE Multimodal observation \(\mathcal{O}_{b,n}\), active VUE set
\(\mathcal{U}_b[n]\), previous track set \(\mathcal{R}_{b,n-1}\), previous
binding map \(\pi_{b,n-1}\), and communication measurements when an association
event occurs
\ENSURE Updated tracks \(\mathcal{R}_{b,n}\), binding map \(\pi_{b,n}\), and
CSI-RS candidate sets \(\{\mathcal{C}_{b,u,n}\}_{u\in\mathcal{U}_b[n]}\)
\STATE Construct the distributed multimodal BEV feature \(\mathbf{F}_{b,n}\).
\STATE Decode unbound detections and target-level distributions
\(\{(d_{b,i,n},\mathbf{p}_{b,i,n})\}_i\).
    \STATE Mix CV and CT hypotheses, then predict existing tracks using the IMM.
    \STATE Gate and assign current detections to tracks, then update the matched
    states, mode probabilities, confidence, observation history, hint age, and
    current beam distributions.
\IF{an initial-access, serving-cell-change, or reassociation event occurs}
    \STATE Obtain conventional SSB/CSI-RS measurements for the affected VUEs.
    \STATE Form feasible UE--track pairs using SSB-parent consistency.
    \STATE Solve the beam-likelihood assignment with unmatched alternatives.
    \STATE Apply association acceptance tests and update \(\pi_{b,n}\).
\ENDIF
\FOR{each \(u\in\mathcal{U}_b[n]\)}
    \IF{\(\pi_{b,n}(u)\) is accepted, currently observed, and \(G_{u,n}=1\)}
        \STATE Derive fixed or adaptive sensing candidates from the current
        target distribution.
    \ELSE
        \STATE Use conventional refinement candidates.
    \ENDIF
    \STATE Measure the selected CSI-RS candidates and choose the service beam
    from the measured quality.
\ENDFOR
\end{algorithmic}
\end{algorithm}

The principal computational terms have distinct scaling behaviour.  BEV feature
construction depends on the number of camera views, point-cloud observations,
and BEV resolution.  Joint inference produces one \(M_{\mathrm{CSI}}\)-way
distribution per decoded target; its target-level output therefore scales with
the number of detections and the 192-beam codebook.  Detection--track and
UE--track assignments operate on their respective gated candidate sets, and a
standard Hungarian solver has cubic complexity in the larger side of each
assignment.  IMM propagation is linear in the number of active tracks and
motion modes.  In contrast, \(K_{\mathrm{scan}}\) controls air-interface
measurement width rather than sensing-network computation.

This decomposition identifies the variables governing the framework's
algorithmic and measurement burden without asserting an implementation-specific
latency.  Chapter~\ref{ch:experiments} evaluates the resulting perception,
association, candidate-selection, and communication consequences under a common
frozen protocol.
