\chapter{System Model and Problem Formulation}
\label{ch:system-model}

This chapter establishes the system abstraction for distributed multimodal
sensing-assisted beam management in a vehicular network.  It distinguishes the
physical vehicle observed by the sensing system from the vehicle user equipment
(VUE) addressed by the communication system, and specifies how the two domains
are coupled through communication measurements.  The presentation proceeds from
the local network architecture and sensing observations to an NR-oriented beam
management procedure, before formulating the coupled perception, association,
and communication objectives.  The learning and inference mechanisms that
realise this model are developed in Chapter~\ref{ch:methodology}.

\section{Network Architecture}
\label{sec:system-network}

Consider a roadside vehicular network with a set of base stations (BSs)
\(\mathcal{B}\).  The formulation is centred on a target BS \(b\in\mathcal{B}\),
which serves the VUEs in its local service region and executes the corresponding
beam-management decisions.  A set \(\mathcal{N}_b\) of neighbouring distributed
sensing nodes (SNs) provides additional camera views of the same road region.
The SNs are sensing-only collaborators: they neither schedule VUEs nor establish
independent service cells in the model.  Thus, all communication measurements,
beam decisions, and association states discussed below are local to the target
BS.

Let \(\mathcal{U}_b[n]\) denote the active VUE set of BS \(b\) at sensing epoch
\(n\).  A member \(u\in\mathcal{U}_b[n]\) has a communication-side identifier
used for synchronisation, measurement reporting, scheduling, and downlink
transmission.  In contrast, the sensing system produces unlabelled physical
targets.  A vehicle that is visible to the sensors is therefore not automatically
known to be a particular VUE, and a VUE can be temporarily unobserved because of
occlusion or a sensing miss.  This distinction makes target-to-user association
an explicit part of the system model rather than an implicit consequence of
detection.

The index \(n\) refers to a sensing epoch, at which observations from the BS and
its SNs are aligned to a common local bird's-eye-view (BEV) frame.  The frame is
anchored at the target BS and covers its local service region.  A VUE entering a
new serving cell establishes a new local association there; no global identity
is assumed to persist across BSs.  The relation between sensing epochs and the
radio timing used for beam management is specified in
Section~\ref{subsec:system-beam-management}.

\section{Multimodal and Distributed Sensing Model}
\label{sec:system-sensing}

At sensing epoch \(n\), the observations available to BS \(b\) combine multiview
images from the BS and its neighbouring SNs with an ISAC-derived point cloud
available locally at the BS.  We write
\begin{equation}
    \mathcal{O}_{b,n}
    = \bigl\{\mathcal{I}_{b,n},\mathcal{I}_{\mathcal{N}_b,n},
    \mathcal{P}_{b,n}\bigr\},
    \label{eq:system-sensing-observation}
\end{equation}
where the three terms respectively denote the target-BS camera observations,
neighbouring-SN camera observations, and the BS-local point cloud.  Sensor
calibration maps every modality into the BEV frame of BS \(b\).  This common
representation permits complementary viewpoints to be used for vehicle
observation, while retaining a BS-centred interpretation of the beam labels.

\subsection{Camera Observations}
\label{subsec:system-camera}

Let \(\mathcal{V}_j\) be the set of cameras mounted at roadside node \(j\).  The
camera observations of the target BS and its collaborating SNs are respectively
written as
\begin{align}
    \mathcal{I}_{b,n} & = \{I_{b,v,n}: v\in\mathcal{V}_b\}, \\
    \mathcal{I}_{\mathcal{N}_b,n} & =
    \{I_{s,v,n}:s\in\mathcal{N}_b,\ v\in\mathcal{V}_s\}.
    \label{eq:system-camera-observations}
\end{align}
Each image is accompanied by fixed camera intrinsics and an extrinsic transform
to the target-BS coordinate system.  The distributed views are not treated as
separate predictions that are combined only after detection.  Instead, they
provide observations of a shared physical scene before the joint detection and
beam-prediction task.  In particular, an SN view can retain evidence of a
vehicle whose target-BS view is partly occluded, whereas the target-BS view
maintains the direct geometric relation to the serving link.

\subsection{ISAC Point-Cloud Model}
\label{subsec:system-isac}

The BS-local ISAC observation is represented as a point cloud
\begin{equation}
    \mathcal{P}_{b,n}=
    \{(\mathbf{q}_{b,m,n},a_{b,m,n})\}_{m=1}^{N^{\mathrm{pc}}_{b,n}},
    \label{eq:system-point-cloud}
\end{equation}
where \(\mathbf{q}_{b,m,n}\) is the position of a sensing point in the local
frame, \(a_{b,m,n}\) denotes optional point attributes, and
\(N^{\mathrm{pc}}_{b,n}\) is the number of retained points.  Its physical origin
can be described by the monostatic echo observation
\begin{equation}
    \mathbf{Y}^{\mathrm{echo}}_{b,n}
    = \mathbf{H}^{\mathrm{echo}}_{b,n}\mathbf{S}_{b,n}
    +\mathbf{N}_{b,n},\qquad
    \mathbf{H}^{\mathrm{echo}}_{b,n}
    =\mathbf{H}^{\mathrm{clu}}_{b,n}
    +\sum_{q\in\mathcal{Q}^{\mathrm{tar}}_{b,n}}
    \mathbf{H}^{\mathrm{tar}}_{b,q,n},
    \label{eq:system-isac-echo}
\end{equation}
where \(\mathbf{S}_{b,n}\) is the transmitted sensing waveform,
\(\mathbf{N}_{b,n}\) is receiver noise, \(\mathbf{H}^{\mathrm{clu}}_{b,n}\)
collects static clutter, and \(\mathcal{Q}^{\mathrm{tar}}_{b,n}\) indexes
target-related multipath components.  With an echo-channel estimate
\(\widehat{\mathbf{H}}^{\mathrm{echo}}_{b,n}\), obtained for example by
correlating the received echo with the known waveform, static-clutter
suppression and point extraction are abstracted as
\begin{equation}
    \widehat{\mathbf{H}}^{\mathrm{echo}}_{b,n}
    =\mathbf{Y}^{\mathrm{echo}}_{b,n}\mathbf{S}^{\dagger}_{b,n},\qquad
    \widetilde{\mathbf{H}}_{b,n}
    =\widehat{\mathbf{H}}^{\mathrm{echo}}_{b,n}
    -\widehat{\mathbf{H}}^{\mathrm{clu}}_{b,n},\qquad
    \mathcal{P}_{b,n}=
    \mathcal{E}_{\mathrm{pc}}\bigl(\widetilde{\mathbf{H}}_{b,n}\bigr).
    \label{eq:system-isac-extraction}
\end{equation}
Equation~\eqref{eq:system-isac-extraction} is an observation abstraction: it
explains how target-related propagation can give rise to a geometric point
cloud, without claiming a complete ISAC waveform or radar signal-processing
implementation.  The point-cloud data used in the evaluation are treated as the
available output of this sensing stage.

\section{Communication Model}
\label{sec:system-communication}

The communication model describes how a target BS converts measured beam and
channel information into multi-user downlink transmission.  It retains the
three functions that are material to the proposed framework: SSB-based coarse
beam identification, CSI-RS-based refinement, and precoded data transmission.
The model is NR-oriented and resource-aware, but it abstracts away detailed
physical-resource-block and control-channel mappings.

\subsection{Downlink Signal and Channel Model}
\label{subsec:system-downlink-model}

Let \(N_b\) denote the number of transmit-antenna elements at BS \(b\), and
let \(\mathcal{U}^{\mathrm{sch}}_b[n]\subseteq\mathcal{U}_b[n]\) be the VUEs
scheduled for downlink transmission in beam-management cycle \(n\).  The
downlink channel from BS \(b\) to VUE \(u\) is denoted by
\(\mathbf{h}_{b,u,n}\in\mathbb{C}^{N_b}\).  Consistent with the ray-tracing
and Doppler abstraction used in the evaluation, it can be represented by a
time-varying geometric channel
\begin{equation}
    \mathbf{h}_{b,u,n}
    =
    \sum_{\ell=1}^{L_{b,u,n}}
    \alpha_{b,u,\ell,n}
    e^{\mathrm{j}2\pi\nu_{b,u,\ell,n}t_n}
    \mathbf{a}_b(\vartheta_{b,u,\ell,n}),
    \label{eq:system-geometric-channel}
\end{equation}
where \(L_{b,u,n}\) is the number of resolved paths,
\(\alpha_{b,u,\ell,n}\), \(\nu_{b,u,\ell,n}\), and
\(\vartheta_{b,u,\ell,n}\) are the complex gain, Doppler frequency, and
departure angle of path \(\ell\), respectively; \(t_n\) is the reference time
of cycle \(n\); and
\(\mathbf{a}_b(\cdot)\) is the transmit-array response.  The system model does
not require a particular channel-estimation implementation; it requires only
that the resulting channel evolution be common to all compared policies.

After beam selection and CSI feedback, let
\(\mathbf{h}^{\mathrm{eff}}_{b,u,n}\in\mathbb{C}^{N_b^{\mathrm{eff}}}\)
denote the effective channel presented to the digital precoder.  With unit-power
data symbol \(s_{b,u,n}\), transmit power \(P_{b,u,n}\), and precoding vector
\(\mathbf{w}_{b,u,n}\), the received signal is
\begin{equation}
    y_{b,u,n}
    =
    \sqrt{P_{b,u,n}}
    \bigl(\mathbf{h}^{\mathrm{eff}}_{b,u,n}\bigr)^{\mathrm{H}}
    \mathbf{w}_{b,u,n}s_{b,u,n}
    +
    \sum_{v\in\mathcal{U}^{\mathrm{sch}}_b[n]\setminus\{u\}}
    \sqrt{P_{b,v,n}}
    \bigl(\mathbf{h}^{\mathrm{eff}}_{b,u,n}\bigr)^{\mathrm{H}}
    \mathbf{w}_{b,v,n}s_{b,v,n}
    +z_{b,u,n},
    \label{eq:system-downlink-signal}
\end{equation}
where \(z_{b,u,n}\sim\mathcal{CN}(0,\sigma^2_{b,u,n})\).  The corresponding
instantaneous downlink SINR is
\begin{equation}
    \gamma_{b,u,n}
    =
    \frac{P_{b,u,n}
    \left|\bigl(\mathbf{h}^{\mathrm{eff}}_{b,u,n}\bigr)^{\mathrm{H}}
    \mathbf{w}_{b,u,n}\right|^2}
    {\displaystyle
    \sum_{v\in\mathcal{U}^{\mathrm{sch}}_b[n]\setminus\{u\}}
    P_{b,v,n}
    \left|\bigl(\mathbf{h}^{\mathrm{eff}}_{b,u,n}\bigr)^{\mathrm{H}}
    \mathbf{w}_{b,v,n}\right|^2
    +\sigma^2_{b,u,n}}.
    \label{eq:system-downlink-sinr}
\end{equation}

\subsection{Beam Management and Precoding}
\label{subsec:system-beam-management}

The radio-frame duration is \(T_{\mathrm{frame}}=10\,\mathrm{ms}\).  For
subcarrier-spacing numerology \(\mu\), one slot occupies
\begin{equation}
    T_{\mathrm{slot}}=\frac{1}{2^{\mu}}\,\mathrm{ms}.
    \label{eq:system-slot-duration}
\end{equation}
The sensing update interval \(T_{\mathrm{sen}}\), SSB periodicity
\(T_{\mathrm{SSB}}\), and CSI-RS periodicity \(T_{\mathrm{CSI}}\) need not be
identical.  Each sensing epoch is associated with a beam-management cycle that
uses the most recent sensing observation and the communication measurements
available in the corresponding radio interval.  The concrete periodicities are
fixed consistently across policies in the evaluation.

For BS \(b\), let \(\mathcal{F}^{\mathrm{SSB}}_b\) and
\(\mathcal{F}^{\mathrm{CSI}}_b\) denote the SSB and CSI-RS beam codebooks, with
\(M_{\mathrm{SSB}}=48\) and \(M_{\mathrm{CSI}}=192\) entries, respectively.
Each CSI-RS beam \(k\in\{1,\ldots,M_{\mathrm{CSI}}\}\) has an SSB parent
\(\varphi_b(k)\in\{1,\ldots,M_{\mathrm{SSB}}\}\).  The physical gain of this
beam for VUE \(u\) is
\begin{equation}
    g_{b,u,n}(k)
    =
    \left|\mathbf{h}^{\mathrm{H}}_{b,u,n}
    \mathbf{f}^{\mathrm{CSI}}_{b,k}\right|^2,
    \qquad k\in\{1,\ldots,M_{\mathrm{CSI}}\},
    \label{eq:system-beam-gain}
\end{equation}
where \(\mathbf{f}^{\mathrm{CSI}}_{b,k}\) is the corresponding codebook vector.
The strongest physical beam, \(\arg\max_k g_{b,u,n}(k)\), supplies the Top-1
label used by the beam classifier; it is not directly available to the online
decision procedure.

Conventional beam management first obtains an SSB measurement for coarse
serving-beam identification, then measures a CSI-RS candidate set
\(\mathcal{C}_{b,u,n}\) for narrow-beam refinement.  Initial access, a
serving-cell change, and a loss of association reliability all invoke this
conventional measurement path.  When a current perception track has a credible
association with VUE \(u\), the track's beam-class posterior may instead order a
smaller CSI-RS candidate set; the association and candidate constraints are
formalised in Section~\ref{sec:system-problem}.  In either case, the service beam
is selected only from measured CSI-RS responses,
\begin{equation}
    k^{\star}_{b,u,n}
    =
    \underset{k\in\mathcal{C}_{b,u,n}}{\arg\max}\;
    \widetilde{g}_{b,u,n}(k),
    \label{eq:system-service-beam}
\end{equation}
where \(\widetilde{g}_{b,u,n}(k)\) is the measured response.  Thus, the
192-way classifier output ranks measurement candidates, whereas
\(K_{\mathrm{scan}}=|\mathcal{C}_{b,u,n}|\) determines the actual narrow-beam
measurement budget.

Let \(\widehat{\mathbf{H}}_b[n]\) collect the effective-channel estimates of
the scheduled VUEs after this measurement and feedback procedure.  The BS forms
the regularised zero-forcing (RZF) precoder
\begin{equation}
    \mathbf{W}_b[n]
    =
    \widehat{\mathbf{H}}_b^{\mathrm{H}}[n]
    \left(\widehat{\mathbf{H}}_b[n]
    \widehat{\mathbf{H}}_b^{\mathrm{H}}[n]
    +\lambda_b\mathbf{I}\right)^{-1}\mathbf{D}_b[n],
    \label{eq:system-rzf-precoder}
\end{equation}
where \(\lambda_b\) is the regularisation factor and \(\mathbf{D}_b[n]\)
normalises the RZF columns.  The columns of \(\mathbf{W}_b[n]\) provide the
precoding directions in Equation~\eqref{eq:system-downlink-signal}, while
\(P_{b,u,n}\) specifies their allocated powers; substituting them into
Equation~\eqref{eq:system-downlink-sinr} yields
\(\gamma^{\mathrm{RZF}}_{b,u,n}\).

\subsection{Resource Overhead and Effective Rate}
\label{subsec:system-resource-rate}

Within a beam-management cycle, the normalised downlink resource budget is
partitioned as
\begin{equation}
    \tau_{b,n}^{\mathrm{tot}}
    =
    \tau_{b,n}^{\mathrm{SSB}}
    +\tau_{b,n}^{\mathrm{CSI\text{-}RS}}
    +\tau_{b,n}^{\mathrm{ctrl}}
    +\tau_{b,n}^{\mathrm{data}}.
    \label{eq:system-resource-budget}
\end{equation}
For the set \(\mathcal{E}_b[n]\) of beam-acquisition events in the cycle, the
CSI-RS resource consumption is represented by
\begin{equation}
    \tau_{b,n}^{\mathrm{CSI\text{-}RS}}
    =
    \sum_{e\in\mathcal{E}_b[n]}
    \left\lceil\frac{K_e}{M}\right\rceil\delta_{\mathrm{probe}},
    \qquad
    \eta_{b,n}^{\mathrm{data}}
    =
    \frac{\tau_{b,n}^{\mathrm{data}}}{\tau_{b,n}^{\mathrm{tot}}},
    \label{eq:system-csirs-overhead}
\end{equation}
where \(K_e\) is the total number of CSI-RS beams measured at event \(e\),
\(M\) is the number of beam measurements that can be multiplexed, and
\(\delta_{\mathrm{probe}}\) is the normalised cost of one acquisition occasion.
The SSB, control, and data terms retain their common roles across policies;
sensing assistance affects the rate only through its effect on the candidate
width \(K_e\), the selected beam, and the resulting effective channel.

Let \(\chi_{b,u,n}\in\{0,1\}\) denote the scheduling indicator of VUE \(u\),
and let \(B_b\) and \(\eta_b^{\mathrm{DL}}\) be the allocated bandwidth and
downlink fraction, respectively.  The overhead-adjusted achievable rate is
defined as
\begin{equation}
    R_{b,u,n}^{\mathrm{ach}}
    =
    \chi_{b,u,n}B_b\eta_b^{\mathrm{DL}}
    \eta_{b,n}^{\mathrm{data}}
    \log_2\!\left(1+\gamma_{b,u,n}^{\mathrm{RZF}}\right).
    \label{eq:system-achievable-rate}
\end{equation}
This definition assigns zero rate to an active VUE that is not scheduled in a
cycle, and therefore supports an all-UE time-average performance measure rather
than a conditional rate over scheduled transmissions alone.

\section{Problem Formulation}
\label{sec:system-problem}

The sensing, association, and beam-management layers operate on different
indices, but their purpose is common: to improve the long-term communication
performance of the active VUE population under a finite measurement budget.  The
problem is therefore formulated as a constrained, causal rate-maximisation
problem.  The following subsection first specifies how target-level sensing
evidence is permitted to enter a VUE-level decision; the final subsection states
the resulting communication objective.

\subsection{Association-Constrained Candidate Selection}
\label{subsec:system-association-candidate}

From \(\mathcal{O}_{b,n}\), the sensing model \(\mathcal{G}_{\theta}\) produces
unbound detections and beam-class posteriors,
\begin{equation}
    \mathcal{G}_{\theta}(\mathcal{O}_{b,n})
    \longmapsto
    \left\{\bigl(d_{b,i,n},\mathbf{p}_{b,i,n}\bigr):
    i\in\mathcal{D}_{b,n}\right\},
    \qquad
    \mathbf{p}_{b,i,n}\in[0,1]^{M_{\mathrm{CSI}}},\qquad
    \sum_{k=1}^{M_{\mathrm{CSI}}}p_{b,i,n}(k)=1.
    \label{eq:system-perception-mapping}
\end{equation}
Here, \(d_{b,i,n}\) is a physical-target detection and
\(\mathbf{p}_{b,i,n}\) is its 192-class beam posterior.  Neither output carries
a communication identity.  Let \(\mathcal{R}^{\mathrm{obs}}_{b,n}\) be the set
of currently observed perception tracks maintained from these detections.  The
target-to-user association is a partial one-to-one mapping
\begin{equation}
    \pi_{b,n}:\mathcal{U}_b[n]\longrightarrow
    \mathcal{R}^{\mathrm{obs}}_{b,n}\cup\{\varnothing\},
    \qquad
    \sum_{u\in\mathcal{U}_b[n]}
    \mathbf{1}\!\left\{\pi_{b,n}(u)=r\right\}\leq 1,
    \quad \forall r\in\mathcal{R}^{\mathrm{obs}}_{b,n},
    \label{eq:system-association-map}
\end{equation}
where \(\pi_{b,n}(u)=\varnothing\) means that no sensing-derived hint is
accepted for VUE \(u\).

At an association event, conventional measurements provide a serving SSB
\(s_{b,u,n}\) and a VUE-indexed CSI-RS measurement \(\kappa_{b,u,n}\).  If
track \(r\) carries posterior \(\mathbf{p}_{r,n}\), its compatibility with VUE
\(u\) is measured by
\begin{equation}
    c_{u,r,n}
    =
    -\frac{\log\!\left(p_{r,n}\bigl(\kappa_{b,u,n}\bigr)+\epsilon\right)}
    {\log M_{\mathrm{CSI}}},
    \qquad
    \varphi_b\bigl(\kappa_{b,u,n}\bigr)=s_{b,u,n},
    \label{eq:system-association-cost}
\end{equation}
where \(\epsilon>0\) is a numerical constant.  The parent condition defines
the feasible UE--track pairs; a one-to-one assignment with unmatched choices
determines \(\pi_{b,n}\).  This construction ensures that sensing evidence is
attached to a VUE through communication-side evidence rather than by a direct
geometric or identity inference.

Let \(G_{u,n}\in\{0,1\}\) denote the reliability decision derived from the
accepted association, current track observation, association margin, detection
and track confidence, hint age, and posterior-score concentration.  The
candidate policy is
\begin{equation}
    \mathcal{C}_{b,u,n}
    =
    \begin{cases}
        \operatorname{TopK}_{K_{\mathrm{scan}}}
        \left(\mathbf{p}_{\pi_{b,n}(u),n}\right),
        &G_{u,n}=1,\ \pi_{b,n}(u)\in\mathcal{R}^{\mathrm{obs}}_{b,n},\\
        \mathcal{C}^{\mathrm{conv}}_{b,u,n}, &\text{otherwise},
    \end{cases}
    \label{eq:system-candidate-policy}
\end{equation}
where \(\mathcal{C}^{\mathrm{conv}}_{b,u,n}\) is supplied by conventional
refinement.  Thus, a sensing prediction can reduce CSI-RS measurements only for
a current, accepted UE--track association; the final service beam remains the
measured choice in Equation~\eqref{eq:system-service-beam}.

\subsection{Long-Term Average-Rate Maximisation}
\label{subsec:system-long-term-rate}

For a horizon of \(N\) beam-management cycles, define the all-UE average
achievable rate of BS \(b\) as
\begin{equation}
    \overline{R}_b[N]
    =
    \frac{1}{N}
    \sum_{n=1}^{N}
    \frac{1}{\left|\mathcal{U}_b[n]\right|}
    \sum_{u\in\mathcal{U}_b[n]}
    R_{b,u,n}^{\mathrm{ach}}.
    \label{eq:system-average-rate}
\end{equation}
The operational objective can then be stated as
\begin{align}
    \mathcal{P}_1:\qquad
    \underset{\{\pi_{b,n},\mathcal{C}_{b,u,n},\mathbf{W}_b[n],
    \chi_{b,u,n}\}}{\operatorname{maximise}}\quad
    &\liminf_{N\rightarrow\infty}\overline{R}_b[N]
    \label{eq:system-rate-maximisation}\\
    \text{subject to}\quad
    &\mathcal{C}_{b,u,n}\ \text{satisfies
    Equation~\eqref{eq:system-candidate-policy}},
    \label{eq:system-rate-constraint-candidate}\\
    &k^{\star}_{b,u,n}=\underset{k\in\mathcal{C}_{b,u,n}}{\arg\max}\;
    \widetilde{g}_{b,u,n}(k),
    \label{eq:system-rate-constraint-measurement}\\
    &\tau_{b,n}^{\mathrm{SSB}}+\tau_{b,n}^{\mathrm{CSI\text{-}RS}}
    +\tau_{b,n}^{\mathrm{ctrl}}+\tau_{b,n}^{\mathrm{data}}
    =\tau_{b,n}^{\mathrm{tot}},
    \label{eq:system-rate-constraint-resource}\\
    &\displaystyle\sum_{u\in\mathcal{U}^{\mathrm{sch}}_b[n]}
    P_{b,u,n}\left\|\mathbf{w}_{b,u,n}\right\|^2
    \leq P_b^{\mathrm{max}},
    \qquad \forall n.
    \label{eq:system-rate-constraint-power}
\end{align}
The optimisation is causal: \(\pi_{b,n}\), \(\mathcal{C}_{b,u,n}\),
\(\mathbf{W}_b[n]\), and \(\chi_{b,u,n}\) can depend only on sensing outputs,
track states, and communication measurements available by cycle \(n\).  The
Top-1 beam classifier and IMM tracker supply the causal sensing and tracking
states used in these constraints; their learning and filtering recursions are
specified in Chapter~\ref{ch:methodology}.  Consequently, \(\mathcal{P}_1\)
does not treat oracle identities, unmeasured beam gains, or future channels as
decision inputs.  Its purpose is to make explicit that any candidate reduction
is valuable only insofar as it improves the long-term rate after both
measurement overhead and multi-user interference have been accounted for.
